### 2020-05-25 Draft.tex
t

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyphenat}
\usepackage{enumitem}
\usepackage{graphicx}
\graphicspath{ {./images/} }

% Referencing
\usepackage[authordate,strict,backend=bibtex8,babel=other,bibencoding=inputenc]{biblatex-chicago}
\addbibresource{references}

% Create the Title 
\title{Finding New Pulsars Using Machine Learning}
\author{Jacob Ian Matthews \\ \\ Draft 1}

\begin{document}

% Build the title page
\begin{titlepage}

    \maketitle

    \section*{Abstract}

\end{titlepage}

\pagebreak

% Build Table of Contents
\tableofcontents

\pagebreak

% Start sections

% INTRODUCTION SECTION
\section{Introduction}

\subsection{Aim}

This project consists of three aims:
\begin{enumerate}[label=\roman*.]
    \item Investigate the use of Machine Learning (ML) techniques in surveying pulsars;
    \item Create a training dataset for a Machine Learning algorithm to find pulsars in data obtained by the Murchison Widefield Array (MWA); and
    \item Evaluate the utility of the Machine Learning algorithm used by the LOFAR Telescope for the Murchison Widefield Array, and adjust the algorithm as necessary to achieve optimum pulsar candidate generation.
\end{enumerate}

\subsection{Structure of this Report}

In this report, I will first explain in \emph{Section 1.3} how Pulsars, Radio Astronomy, and Machine learning work, and then explain what has been dubbed the ``Candidate Selection Problem" \autocite{lyon} and why Machine Learning is necessary in completing future pulsar surveys.

In \emph{Section 2} I discuss the methods undertook in: (i) developing the machine learning training dataset for the Murchison Widefield Array algorithm, and (ii) evaluating the machine learning algorithm used by the LOFAR surveys for use with the Murchison Widefield Array.

In \emph{Section 3} I analyse the results and findings obtained by the methods described in \emph{Section 2}, and in \emph{Section 4} I will discuss (i) the efficacy of the training datasets, and (ii) the usefulness of the LOFAR machine learning algorithm with the Murchison Widefield Array and why changes were made to the algorithm.

This report will end with my final conclusions on the use of machine learning in discovering new pulsars (\emph{Section 5}), and my recommendations to future researchers undertaking a similar project (\emph{Section 6}).

\subsection{Background Theory}

To answer the question of "what is a pulsar?" we must first investigate the evolution and death of stars.

A star can form when a cloud of hydrogen gas in the interstellar medium (ISM) collects mass over millions of years; as the mass of the gas cloud increases, its gravitational pull to gather more mass also increases \autocite{maoz}. This proto-star will eventually reach a critical mass in which the pressure of gravity within the gas causes enough friction between the gas particles to generate the required heat (thermal pressure) to begin fusing the hydrogen atoms into helium \autocite{maoz}. This marks the beginning of the star's main sequence lifetime. Once the star has fused all of the available hydrogen gas in its core, the star will begin fusing helium into carbon and its outer envelope will expand, moving the star into its "red-giant" phase \autocite{maoz}. If the initial mass of the star was greater than 8 times the mass of the Sun (i.e. $8M_{\odot}$), the star will continue to fuse the elements in its core until it reaches a core of iron. At this point phenomena called nuclear photodisintegration and neutronization occurs, the latter of which causes electrons and photons to combine and form neutrons and anti-neutrinos \autocite{maoz}. Neutronization can be shown as:

$$ e^{-}+p\rightarrow n + \nu_e$$

This process removes the electron degeneracy pressure in the core of the star (a pressure which balances the star's gravitational pressure), causing the star to collapse under its own gravity in a timeframe of 0.1 seconds \autocite{maoz}. The gravitational collapse stops once the gravitational pressure of the star is balanced by the neutron degeneracy pressure, i.e. the pressure from pushing neutrons together. The remaining star is incredibly dense, with a mass of approximately $1.4M_{\odot}$ and a radius of around 11km. This is called a neutron star \autocite{maoz}.

Prior to the collapse of the star, we can imagine the star to be rotating at an angular velocity of $\omega_1$. We know from the conservation of angular momentum that when the radius of a rotating object decreases, the angular velocity will increase (a spinning ice skater pulling their arms in close increases the speed of their spinning). We can therefore show that the angular velocity of the star after the gravitational collapse, $\omega_2$, is much greater than the prior angular velocity:

$$L_1 = L_2$$ where $L$ is the angular momentum, $L_1=I_1\omega_1$ and $L_2=I_2\omega_2$. Therefore:

$$ I_1 \omega_1 = I_2 \omega_2 $$

$$\omega_2 = \frac{I_1}{I_2}\omega_1$$

Assuming the star is a sphere, its moment of inertia, $I$ is:

$$I = \frac{2}{5}MR^2$$ where $M$ is the mass of the star and $R$ is the radius of the star. We can thus show:

$$\omega_2 = \frac{\frac{2}{5}MR_1^2}{\frac{2}{5}MR_2^2}\omega_1$$

$$\omega_2 = \left(\frac{R_1}{R_2}\right)^2\omega_1$$ where $R_1 \gg R_2$. We are left with a neutron star with a very large angular velocity. Analogous to the angular velocity of the star, the magnetic field of the star is also amplified. The ionised gas in the iron core of the star, which generates a magnetic field, is compressed by the gravitational collapse, forcing the flux of the magnetic field to be amplified such that the field strength is approximately $10^{10}$ times stronger in the neutron star compared to during the star's main sequence lifetime \autocite{maoz}.

If the rotation of the neutron star is misaligned with the axis of the magnetic field by an angle $\theta$, the spinning magnetic dipole will radiate electromagnetic waves \autocite{maoz}. As the neutron star rotates, the radiated electromagnetic waves will periodically sweep across the line of sight of an observer, creating a pulse of light. See Figure \ref{fig:pulsar1}. We can therefore define a pulsar as a rapidly rotating neutron star that appears to periodically emit electromagnetic waves \autocite{maoz,lorimer,swainston}.

\begin{figure}[h!]
    \centering
    \includegraphics{pulsar.jpg}
    \caption{A pulsar \autocite{maoz}.}
    \label{fig:pulsar1}
\end{figure}

While some pulsars, like the Crab Pulsar \autocite{maoz}, emit electromagnetic waves in the visible spectrum and can therefore be detected by an optical telescope, the majority of pulsar emission is invisible to the human eye and requires a radio telescope to be detected.

\subsubsection{What is a Pulsar Profile?}
\subsubsection{What is multi-path scattering?}
\subsubsection{What is a Pulsar Dispersion Measure?}
\subsubsection{What is a Radio Telescope and how do they work?}
\subsubsection{What is the Murchison Widefield Array?}
\subsubsection{Why are we conducting sky surveys?}
\subsubsection{How is a sky survey conducted with the Murchison Widefield Array?}
\subsubsection{What is tied-array beamforming?}
\subsubsection{How many Pulsar candidates are found in a Murchison Widefield Array sky survey?}
\subsubsection{How long do sky surveys take?}
\subsubsection{How much data is created from a sky survey?}
\subsubsection{What is Radio Frequency Interference?}
\subsubsection{What is a Signal-to-Noise Ratio?}
\subsubsection{What is PRESTO and a .PFD file?}
\subsubsection{What is Machine Learning?}
\subsubsection{How does Machine Learning work?}
\subsubsection{Why do we need to use Machine Learning in finding new Pulsars?}
\subsubsection{Why is this particular Machine Learning Classifier used?}

\pagebreak
% Methods Section
\section{Methods}
\subsection{Developing the Machine Learning Training Dataset}

Before a machine learning algorithm can make predictions and classify candidate data as pulsar or non-pulsar, it must first build a classification model from a training dataset which contains similar data with known positive and negative classifications \autocite{tan, lyon}. For the use case of pulsar classification, the training dataset must contain examples of data from both pulsars and from non-pulsars so that the algorithm can learn how to distinguish between the two classes.

To maximise the accuracy of the machine learning algorithm, the input data (including the training dataset) must be composed of a common group of features that can be determined for each candidate that maximises the differences between a pulsar and a non-pulsar. The candidate features used by \smartcite{tan} to maximise the differences between pulsar and non-pulsar candidates are:

\begin{equation}
    Prof_{\mu}, Prof_{\sigma}, Prof_{S}, Prof_{k}
\end{equation}

\begin{equation}
    DM_{\mu}, DM_{\sigma}, DM_{S},DM_{k},
    DM_{\mu'}, DM_{\sigma'}, DM_{|S'|},DM_{k'}
\end{equation}

\begin{equation}
    Subband_{\mu}, Subband_{\sigma}, Subband_{S}, Subband_{k}
\end{equation}

\begin{equation}
    Subint_{\mu}, Subint_{\sigma}, Subint_{S}, Subint_{k}
\end{equation}

Where features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile. See \emph{Appendix 2A} for formulae to calculate each feature.

To extract the 20 above features from each classification candidate, we can use the software 
\verb|PulsarFeatureLab| \autocite{lyon}.

\subsubsection{Pulsar Candidate Feature Extraction}

The software tool \verb|PulsarFeatureLab| can be used to consume pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.

To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software are unaffected by the host operating system, a containerised virtual operating system can be created using the free software Docker (\verb|https://docker.com|).

First a directory to store the program and the Dockerfile is created by completing the following commands in a UNIX terminal:

\begin{center}
\begin{verbatim}
    $ mkdir ~/pulsars
    $ cd ~/pulsars
    $ touch Dockerfile
\end{verbatim}
\end{center}

\subsection{Evaluating the LOTAAS Machine Learning Algorithm for use with the MWA}

\pagebreak
% Results Section
\section{Results}
\subsection{Pulsar Candidate Training Dataset}
\subsection{Radio Frequency Interference Training Dataset}
\subsection{Noise Training Dataset}
\subsection{Output from Algorithm with MWA Data}
\subsection{Adaptations to the Machine Learning Algorithm}

\pagebreak
% Results Discussion Section
\section{Discussion}
\subsection{How effective are the training datasets?}
\subsection{Why didn't the LOFAR Machine Learning Algorithm work with the MWA?}
\subsection{What changes to the algorithm were necessary for it to successfully classify Pulsars from the MWA?}

\pagebreak
% FINAL CONCLUSTIONS SECTION
\section{Conclusions}

% RECOMMENDATIONS SECTION
\section{Recommendations}

\pagebreak
% REFERENCES SECTION
\section{References}
\printbibliography[heading=none]

\pagebreak
% APPENDICES SECTION
\section{Appendices}
\subsection{Pulsar Feature Lab}
\subsection{Pulsar Classifier}

% End the document
\end{document}

### 2020-05-25 Draft.tex
initial commit

@@
 
-In this report, I will first explain in \emph{Section 1.3} how Pulsars, Radio Astronomy, and Machine learning work, and then explain what has been dubbed the ``Candidate Selection Problem" \autocite{lyon} and why Machine Learning is necessary in completing future pulsar surveys.
+In this report, I will first explain in \emph{Section 1.3} how Pulsars, Radio Astronomy, and Machine learning work, and then explain what has been dubbed the "Candidate Selection Problem" \autocite{lyon} and why Machine Learning is necessary in completing future pulsar surveys.
 
@@
 
-$$\omega_2 = \left(\frac{R_1}{R_2}\right)^2\omega_1$$ where $R_1 \gg R_2$.
+$$\omega_2 = \left(\frac{R_1}{R_2}\right)^2\omega_1$$ where $R_1 >> R_2$.
 We are left with a neutron star with a very large angular velocity.
@@
 \section{Methods}
-\subsection{Developing the Machine Learning Training Dataset}
-
-Before a machine learning algorithm can make predictions and classify candidate data as pulsar or non-pulsar, it must first build a classification model from a training dataset which contains similar data with known positive and negative classifications \autocite{tan, lyon}.
-For the use case of pulsar classification, the training dataset must contain examples of data from both pulsars and from non-pulsars so that the algorithm can learn how to distinguish between the two classes.
-
-To maximise the accuracy of the machine learning algorithm, the input data (including the training dataset) must be composed of a common group of features that can be determined for each candidate that maximises the differences between a pulsar and a non-pulsar.
-The candidate features used by \smartcite{tan} to maximise the differences between pulsar and non-pulsar candidates are:
-
-\begin{equation}
-    Prof_{\mu}, Prof_{\sigma}, Prof_{S}, Prof_{k}
-\end{equation}
-
-\begin{equation}
-    DM_{\mu}, DM_{\sigma}, DM_{S},DM_{k},
-    DM_{\mu'}, DM_{\sigma'}, DM_{|S'|},DM_{k'}
-\end{equation}
-
-\begin{equation}
-    Subband_{\mu}, Subband_{\sigma}, Subband_{S}, Subband_{k}
-\end{equation}
-
-\begin{equation}
-    Subint_{\mu}, Subint_{\sigma}, Subint_{S}, Subint_{k}
-\end{equation}
-
-Where features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile.
-See \emph{Appendix 2A} for formulae to calculate each feature.
-
-To extract the 20 above features from each classification candidate, we can use the software 
-\verb|PulsarFeatureLab| \autocite{lyon}.
-
-\subsubsection{Pulsar Candidate Feature Extraction}
-
-The software tool \verb|PulsarFeatureLab| can be used to consume pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
-
-To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software are unaffected by the host operating system, a containerised virtual operating system can be created using the free software Docker (\verb|https://docker.com|).
-
-First a directory to store the program and the Dockerfile is created by completing the following commands in a UNIX terminal:
-
-\begin{center}
-\begin{verbatim}
-    $ mkdir ~/pulsars
-    $ cd ~/pulsars
-    $ touch Dockerfile
-\end{verbatim}
-\end{center}
-
-\subsection{Evaluating the LOTAAS Machine Learning Algorithm for use with the MWA}
+\subsection{Developing the MWA Machine Learning Training\\ Datasets}
+\subsubsection{Pulsar Candidate Training Datasets}
+\subsubsection{RFI Training Dataset}
+\subsubsection{Noise Training Dataset}
+\subsection{Evaluating the LOFAR Machine Learning Algorithm for use with the MWA}
 
@@
 \subsection{Noise Training Dataset}
-\subsection{Output from Algorithm with MWA Data}
+\subsection{Output from LOFAR Algorithm with MWA Data}
 \subsection{Adaptations to the Machine Learning Algorithm}

### 2020-05-25 Draft.tex
methods

--- 2020-05-25 Draft.tex
@@
 \usepackage{graphicx}
+
+% Coding packages
+\usepackage{listings}
+\usepackage{lmodern}
+\usepackage{xcolor}
+\lstset{
+  basicstyle=\ttfamily,
+  literate={~} {\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}{1},
+  columns=fullflexible,
+  frame=single,
+  breaklines=true,
+  numbers=left,
+  stepnumber=1,
+  xleftmargin=2em,
+  framexleftmargin=1.5em
+}
+
 \graphicspath{ {./images/} }
@@
 
-Before a machine learning algorithm can make predictions and classify candidate data as pulsar or non-pulsar, it must first build a classification model from a training dataset which contains similar data with known positive and negative classifications \autocite{tan, lyon}.
+Before a machine learning algorithm can make predictions and classify candidates as a pulsar or a non-pulsar, it must first build a classification model from a training dataset which contains similar data with known positive and negative classifications \autocite{tan, lyon}.
 For the use case of pulsar classification, the training dataset must contain examples of data from both pulsars and from non-pulsars so that the algorithm can learn how to distinguish between the two classes.
@@
 
-Where features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile.
+Where candidate features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile.
 See \emph{Appendix 2A} for formulae to calculate each feature.
@@
 
-The software tool \verb|PulsarFeatureLab| can be used to consume pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
+The Python software tool \verb|PulsarFeatureLab| can be used to consume pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
 
@@
 
-First a directory to store the program and the Dockerfile is created by completing the following commands in a UNIX terminal:
+First, a directory to store the Dockerfile and pulsar candidate data is created by completing the following commands in a UNIX terminal:
 
-\begin{center}
-\begin{verbatim}
+\begin{lstlisting}[numbers=none]
 $ mkdir ~/pulsars
@@
 $ touch Dockerfile
-\end{verbatim}
-\end{center}
+\end{lstlisting}
 
-\subsection{Evaluating the LOTAAS Machine Learning Algorithm for use with the MWA}
+To create the Docker image, the contents of the \verb|Dockerfile| can be edited to contain:
+
+\begin{lstlisting}[title=Dockerfile]
+FROM alpine/git:latest as builder
+WORKDIR /root/
+RUN cd /root/ && git clone --single-branch --branch V1.3.2 https://github.com/scienceguyrob/PulsarFeatureLab.git && mkdir PulsarFeatureLab/PulsarFeatureLab/Data/IO
+
+FROM python:2.7
+WORKDIR /usr/src/app
+COPY --from=builder /root/PulsarFeatureLab .
+RUN pip install numpy scipy matplotlib astropy
+ENTRYPOINT ["python", "./PulsarFeatureLab/Src/PulsarFeatureLab.py"]
+\end{lstlisting}
+
+The above \verb|Dockerfile| instructs Docker to:
+\begin{enumerate}[label=\roman*.]
+    \item use an image of Alpine Linux with \verb|git| preinstalled to download the \verb|PulsarFeatureLab| software from GitHub \\(\verb|https://github.com/scienceguyrob/PulsarFeatureLab|);
+    \item create a directory inside the downloaded software to store the input and output data;
+    \item create a Docker image based on Python 2.7;
+    \item transfer the \verb|PulsarFeatureLab| software into the Python 2.7 image; and
+    \item install \verb|PulsarFeatureLab|'s library dependencies (\verb|NumPy, SciPy, matplotlib| and \verb|astropy|).
+\end{enumerate}
+
+The above Docker image can now be built into a container (a virtual operating system) and a directory to hold the input data can be created by running the following commands on a UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ docker build -t jacobianm/pulsarfeaturelab:1.3.2 .
+$ mkdir ~/pulsars/data/pfd
+\end{lstlisting}
+
+Candidate \verb|PFD| files of known pulsars and non-pulsars detected by the Murchison Widefield Array (MWA) provided by N.
+Swainston can now populate the above created directory, and the following command can be ran to extract the features from the candidates:
+
+\begin{lstlisting}[numbers=none]
+$ docker run --rm -v ~/pulsars/data/pfd:/usr/src/app/PulsarFeatureLab/Data/IO jacobianm/pulsarfeaturelab:1.3.2 -d "/usr/src/app/PulsarFeatureLab/Data/IO" -c 3 -t 6 -f "/usr/src/app/PulsarFeatureLab/Data/IO/output.arff" --arff --meta
+\end{lstlisting}
+
+This function instructs Docker to connect the directory containing the \verb|PFD| files to the \verb|PulsarFeatureLab| container's input/output directory and then run the \verb|PulsarFeatureLab| software with arguments stating where the input files are, what filetype they are (\verb|PFD|), which set of features to extract, and where to place the output file.
+
+\subsubsection{Creating the Training Dataset}
+
+The \verb|output.arff| file created by \verb|PulsarFeatureLab|, contains a set of comma-separated features for each candidate, with an appended `?' character, per file line.
+Since the class of each candidate is already known, the `?' character on each line can be replaced by a `1' if the candidate is a pulsar, or a `0' if the candidate is a non-pulsar.
+This signals to the Machine Learning algorithm what a pulsar and a non-pulsar candidate's feature set may appear like.
+
+The edited file can now be renamed and moved with the following command:
+
+\begin{lstlisting}[numbers=none]
+$ mv ~/pulsars/data/pfd/output.arff ~/pulsars/data/trainingSet.arff
+\end{lstlisting}
+
+The Machine Learning Training Dataset has now been created using Murchison Widefield Array data.
+\\
+
+\subsection{Evaluating the LOTAASClassifier Machine Learning Classification Tool for use with the Murchison Widefield Array}
 
@@
 % Results Section
-\section{Results}
-\subsection{Pulsar Candidate Training Dataset}
-\subsection{Radio Frequency Interference Training Dataset}
-\subsection{Noise Training Dataset}
-\subsection{Output from Algorithm with MWA Data}
-\subsection{Adaptations to the Machine Learning Algorithm}
+\section{Results and Outputs}
+\subsection{Machine Learning Training Dataset}
+
+The machine learning training dataset created with candidates detected by the Murchison Widefield Array is as follows:
+
+\begin{lstlisting}[title=trainingSet.arff]
+
+\end{lstlisting}
+
+\subsection{Output from LOTAASClassifier with Murchison Widefield Array Data}
+\subsection{Output from PulsarClassifier Machine Learning Classification Tool}
 

### 2020-05-25 Draft.tex
methods

@@
 \usepackage{xcolor}
+\usepackage{algorithmicx}
 \lstset{
@@
 \title{Finding New Pulsars Using Machine Learning}
-\author{Jacob Ian Matthews \\ \\ Draft 1}
+\author{Jacob Ian Matthews \\ \\ Draft}
 
@@
 The Machine Learning Training Dataset has now been created using Murchison Widefield Array data.
-\\
 
 \subsection{Evaluating the LOTAASClassifier Machine Learning Classification Tool for use with the Murchison Widefield Array}
+
+To address the Candidate Selection Problem discussed in \emph{Section 1.3} of this report, a Java Machine Learning pulsar classification tool named \verb|LOTAASClassifier| was created to classify the pulsar candidates produced by the LOFAR Tied-Array All-sky Survey (LOTAAS) \autocite{lyon}.
+Due to the similarities between the LOFAR radio telescope and the Murchison Widefield Array (MWA) radio telescope, it is logical to attempt to apply the \verb|LOTAASClassifier| tool to candidates produced by the MWA.
+
+The \verb|LOTAASClassifier| tool contains four machine learning algorithms with which the user can choose to make pulsar classifications.
+They are: the J48 (C4.5 Decision Tree \autocite{quinlan}), the Multi-Layer Perceptron, the Naive Bayes, and the Support Vector Machines (SVM) algorithms \autocite{lyon}.
+
+To begin evaluating the software, \verb|LOTAASClassifier v1.0| can be downloaded from its GitHub repository \\(\verb|https://github.com/scienceguyrob/LOTAASClassifier|) with the following UNIX terminal commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ git clone https://github.com/scienceguyrob/LOTAASClassifier.git
+\end{lstlisting}
+
+The tool's executable program can then be found by navigating to the following directory in the UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/LOTAASClassifier/dist
+\end{lstlisting}
+
+\subsubsection{Creating a Classification Model}
+
+In order to use \verb|LOTAASClassifier| to classify Murchison Widefield Array candidates, we must use the Machine Learning Training Dataset created in \emph{Section 2.1} to create a classification model.
+This can be completed by running the following commands:
+
+\begin{lstlisting}[numbers=none]
+$ java -jar LOTAASClassifier.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/model.m -a 1
+\end{lstlisting}
+
+This instructs \verb|LOTAASClassifier| to create a new classification model for the J48 machine learning algorithm with the previously constructed training dataset.
+
+To ensure that the classification model was created successfully, we can test the model against the same dataset provided by N.
+Swainston to create the training dataset.
+Using \verb|PulsarFeatureLab| we can produce a new \verb|output.arff| file with the candidates' class unedited.
+
+\begin{lstlisting}[numbers=none]
+$ docker run --rm -v ~/pulsars/data/pfd:/usr/src/app/PulsarFeatureLab/Data/IO jacobianm/pulsarfeaturelab:1.3.2 -d "/usr/src/app/PulsarFeatureLab/Data/IO" -c 3 -t 6 -f "/usr/src/app/PulsarFeatureLab/Data/IO/output.arff" --arff --meta
+\end{lstlisting}
+
+It is now possible to test the classification model with the candidate feature sets with the following commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/LOTAASClassifier/dist
+$ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
+\end{lstlisting}
+
+The \verb|LOTAASClassifier| tool will output two files: `\verb|output.positive|' and `\verb|output.negative|', in the same location as the input dataset.
+The J48 classification model was constructed successfully if the candidates inside the `\verb|positive|' file are the known pulsars.
+
+\subsubsection{Evaluating LOTAASClassifier}
+
+With a successfully created machine learning classification model, it is now possible to test \verb|LOTAASClassifier| against a previously unseen (by the classifier) dataset of Murchison Widefield Array candidates whose class is also known.
+We can first remove the existing candidates from inside the \verb|PFD| files directory and delete the existing \verb|output| files.
+
+The candidates directory can then be populated by new \verb|PFD| files and we can use the `\verb|docker run|' command from \emph{Section 2.2.1} to extract the features from the new candidates.
+
+The \verb|LOTAASClassifier| tool can now make classification predictions on the new candidates by running the UNIX terminal command:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/LOTAASClassifier/dist
+$ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
+\end{lstlisting}
+
+By inspecting the created `\verb|output.positive|' and `\verb|output.negative|' files and comparing the results to the known pulsars, we can evaluate the performance of the \verb|LOTAASClassifier| tool with Murchison Widefield Array data and make a judgement about further use of the classifier.
+
+\subsubsection{Creating the PulsarClassifier Ensemble Classification Tool}
+
+According to \cite{tan}, using Machine Learning algorithms in ensemble to make pulsar classifications increases the accuracy of classifications, classifying pulsars that were often misclassified such as wide-pulse pulsars.
+
+To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ mkdir PulsarClassifier && cd PulsarClassifier
+$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
+\end{lstlisting}
+
+We can now copy the source code from \verb|LOTAASClassifier| to be included in the \verb|PulsarClassifier| software.
+
+\begin{lstlisting}[numbers=none]
+$ cp -R ~/pulsars/LOTAASClassifier/src/ ~/pulsars/PulsarClassifier/src/main/java
+\end{lstlisting}
+
+To use the WEKA suite of Machine Learning tools, we must then edit the \verb|pom.xml| file inside \verb|PulsarClassifier| to include it as a dependency, and resynchronise the project:\\
+
+\begin{lstlisting}[numbers=none, title=pom.xml, language=xml]
+...
+<dependencies>
+...
+    <dependency>
+        <groupId>nz.ac.waikato.cms.weka</groupId>
+        <artifactId>weka-stable</artifactId>
+        <version>3.8.0</version>
+    </dependency>
+...
+</dependencies>
+...
+\end{lstlisting}
+
+We now have the following basic project directory structure:
+
+\begin{lstlisting}[numbers=none]
+PulsarClassifier/
+    src/
+        main/
+            java/
+                com/jacobianmatthews/pulsarclassifier/
+                com/scienceguyrob/lotaasclassifier/
+        test/
+            java/
+                com/jacobianmatthews/pulsarclassifier
+    target/
+            ...
+    pom.xml
+\end{lstlisting}
+
+Where the new source code will be located under \\\verb|/src/main/java/com/jacobianmatthews/pulsarclassifier|.
+To introduce the ensemble classification feature, we must write four main Java classes: \\\verb|PulsarClassifier.java|,  \verb|ClassifierBuilder.java|,  \verb|ClassifierValidator.java|,  and \verb|ClassPredictor.java|.
+
+The \verb|LOTAASClassifier| tool accepts a command-line argument \verb|-a| which accepts an integer that denotes the machine learning algorithm to use in building a classification model and making predictions \autocite{lyon}.
+Therefore, we will add an algorithm into the above listed Java classes that will accept an integer value of \verb|-1| that will activate the ensemble classifier.
+
+To add ensemble classification to the class \verb|ClassifierBuilder.java|, we will use the following algorithm:
+
+\begin{algorithmic}[1]
+
+\end{algorithmic}
+
+\subsubsection{Evaluating PulsarClassifier}
 
@@
 
-The machine learning training dataset created with candidates detected by the Murchison Widefield Array is as follows:
-
-\begin{lstlisting}[title=trainingSet.arff]
-
-\end{lstlisting}
+The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix 8.3}.
 
@@
 \subsection{How effective are the training datasets?}
-\subsection{Why didn't the LOFAR Machine Learning Algorithm work with the MWA?}
+\subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
+\subsection{Why did/didn't the LOFAR Machine Learning Algorithm work with the MWA?}
 \subsection{What changes to the algorithm were necessary for it to successfully classify Pulsars from the MWA?}
@@
 
+\pagebreak
+\subsection{Machine Learning Training Dataset}
+\lstinputlisting[title=trainingData.arff, basicstyle=\footnotesize\ttfamily, breaklines=true]{code/trainingSet.arff}
+
 % End the document

### 2020-05-30 Draft.tex
Methods, results, recommendations

@@
 \usepackage{xcolor}
-\usepackage{algorithmicx}
+\usepackage{algorithm, algpseudocode}
 \lstset{
@@
 
+\subsubsection{Creating a Pulsar Classifier Output Validation Tool}
+
+In order to accurately evaluate and test the predictions made by the \verb|LOTAASClassifier| tool, we must create a program that will automate the process of checking the outputs of the classifier against the known list of pulsars.
+
+We begin by creating a new Java project using the free software Maven (\verb|https://maven.apache.org|) by running the following commands in a UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ mkdir PulsarValidator && cd PulsarValidator
+$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
+\end{lstlisting}
+
+We can then create the following file structure and resynchronise the project:
+
+\begin{lstlisting}[numbers=none]
+PulsarValidator/
+    src/
+        main/
+            java/
+                com/jacobianmatthews/pulsarvalidator/
+                    PulsarValidator.java
+        test/
+            ...
+    target/
+            ...
+    pom.xml
+\end{lstlisting}
+
+The file: \verb|PulsarValidator.java| stands as the entry-point to the software and will be compiled into an executable \verb|JAR| file upon completion of creating the software.
+
+This software will consume a user inputted \verb|String| containing the path to a file with the list of pulsars included in the dataset classified by the machine learning classifier, a user inputted \verb|String| containing the path to the \verb|.positive| file created by the classifier, and a user inputted \verb|String| containing the path to the \verb|.negative| file created by the classifier\footnote{The '.positive' file contains the candidates classified as pulsars, and the '.negative' file contains the candidates classified as non-pulsars.}.
+These will be inputted as command-line arguments when the user runs the Java executable file.
+
+To access the user inputted arguments, we can include the following function in the \verb|main(String[] args)| method of the \verb|PulsarValidator.java| class:
+
+\begin{algorithm}[H]
+    \caption{getCliVariables(args) (pseudocode)}
+    \begin{algorithmic}
+        \For{Integer $i=0\rightarrow$ number of arguments in $args$}
+            \If{$i$th argument in $args$ is "-v"}
+                \State Let Boolean $ValidationMode$ = true
+                \State Let String $pulsarListPath$ = ($i+1$)th argument in $args$
+                \State Let String $classifierPositive$ = ($i+2$)th argument in $args$
+                \State Let String $classifierNegative$ = ($i+3$)th argument in $args$
+            \EndIf
+        \EndFor
+    \end{algorithmic}
+\end{algorithm}
+
+We can then use a simple conditional statement after this function is ran to check if the \verb|Boolean ValidationMode| has been set to \verb|true|, to determine whether to continue the validation.
+The complete Java class \verb|PulsarValidator.java| can be seen in \emph{Appendix 7.2.1}.
+
+We can then create a new Java class, \verb|ValidationMode.java|, with the following algorithm to validate the output of the classifier against the list of pulsars:
+
+\begin{algorithm}[H]
+    \caption{ValidationMode.java (pseudocode)}
+    \begin{algorithmic}
+        \State Let $truePositive$ = new List
+        \State Let $falsePositive$ = new List
+        \State Let $trueNegative$ = new List
+        \State Let $falseNegative$ = new List
+
+        \For{each $item$ in $classifierPositive$ list}
+            \State Let Boolean $found$ = false
+            \State Let Integer $i=0$
+            \While{$found$ is false}
+                \If{$i$th item in $pulsarList$ is $item$}
+                    \State add $item$ to $truePositive$ list
+                    \State $found$ = true
+                \ElsIf{$i$ equals number of items in $pulsarList$}
+                    \State add $item$ to $falsePositive$ list
+                    \State $found$ = true
+                \Else
+                    \State $i$=$i+1$
+                \EndIf
+            \EndWhile
+        \EndFor
+
+        \For{each $item$ in $classifierNegative$ list}
+            \State Let Boolean $found$ = false
+            \State Let Integer $i=0$
+            \While{$found$ is false}
+                \If{$i$th item in $pulsarList$ is $item$}
+                    \State add $item$ to $falseNegative$ list
+                    \State $found$ = true
+                \ElsIf{$i$ equals number of items in $pulsarList$}
+                    \State add $item$ to $truePositive$ list
+                    \State $found$ = true
+                \Else
+                    \State $i$=$i+1$
+                \EndIf
+            \EndWhile
+        \EndFor
+        \State Let $TP$ = number of items in $truePositive$
+        \State Let $TN$ = number of items in $trueNegative$
+        \State Let $FP$ = number of items in $falsePositive$
+        \State Let $FN$ = number of items in $falseNegative$
+        \State Let $Pulsars$ = $TP+FN$
+        \State Let $NonPulsars$ = $TN+FP$
+        \State Output $Pulsars$, $NonPulsars$, $TP$, $FP$, $TN$, $FN$
+    \end{algorithmic}
+\end{algorithm}
+
+The complete Java class for \verb|ValidationMode.java| can be found in \emph{Appendix 7.2.2}, and its supplementary classes in \emph{Appendix 7.2}.
+
+We can now compile the program by first adding the following lines of code to the \verb|pom.xml| file at the root of the Maven project:
+
+\begin{lstlisting}[numbers=none, title=pom.xml]
+<project>
+  ...
+  <build>
+    ...
+    <pluginManagement>
+      ...
+      <plugins>
+        ...
+        <!-- Create a JAR containing the resources and dependencies -->
+        <plugin>
+          <artifactId>maven-assembly-plugin</artifactId>
+          <configuration>
+            <descriptorRefs>
+              <descriptorRef>jar-with-dependencies</descriptorRef>
+            </descriptorRefs>
+            <finalName>${project.artifactId}-${project.version}-full</finalName>
+            <appendAssemblyId>false</appendAssemblyId>
+            <archive>
+              <manifest>
+                <mainClass>com.jacobianmatthews.pulsarvalidator.PulsarValidator</mainClass>
+              </manifest>
+            </archive>
+          </configuration>
+          <executions>
+            <execution>
+                <id>make-my-jar-with-dependenciess</id>
+                <phase>package</phase>
+                <goals>
+                    <goal>single</goal>
+                </goals>
+            </execution>
+          </executions>
+        </plugin>
+      </plugins>
+    </pluginManagement>
+  </build>
+</project>
+\end{lstlisting}
+
+Which instructs Maven to create a single \verb|JAR| file containing the program's dependencies and resources. The program can then be compiled and built by running the command:
+
+\begin{lstlisting}[numbers=none]
+$ mvn assembly:single
+\end{lstlisting}
+
+This will produce the file: \verb|/target/pulsarvalidator-1.0-full.jar|, which is an executable Java program.
+The complete source code for \verb|PulsarValidator| can be found in \emph{Appendix 7.2} or at \\\verb|https://github.com/jacob-ian/PulsarValidator.git|.
+
 \subsubsection{Creating a Classification Model}
@@
 
-By inspecting the created `\verb|output.positive|' and `\verb|output.negative|' files and comparing the results to the known pulsars, we can evaluate the performance of the \verb|LOTAASClassifier| tool with Murchison Widefield Array data and make a judgement about further use of the classifier.
+This can be repeated for each machine learning classifier present in the \verb|LOTAASClassifier| software by changing the argument \verb|-a| from 1 through to 4.
+
+We can now run the \verb|PulsarValidator| program created in \emph{Section 2.2.1} to evaluate the accuracy of \verb|LOTAASClassifier|'s algorithms by running the command:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarValidator/target
+$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_[classifier].positive ~/pulsars/data/pfd/output_[classifier].negative
+\end{lstlisting}
+
+Where the \verb|[classifier]| variable can be changed depending on the name of the classifier algorithm being evaluated.
+The outputted validation statistics can then be compared across the algorithms to determine their usefulness with the Murchison Widefield Array.
 
@@
 
-To add ensemble classification to the class \verb|ClassifierBuilder.java|, we will use the following algorithm:
+The class \verb|ClassifierBuilder.java| handles training and building a classification model. To add ensemble classification to this class we will use the following algorithm:
 
+\begin{algorithm}[H]
+    \caption{ClassifierBuilder (pseudocode)}
     \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State buildClassifier($i$, $trainingSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Build individual classifier
+            \State buildClassifier($algorithm$, $trainingSet$, $modelPath$)
+
+        \EndIf
 
     \end{algorithmic}
+\end{algorithm}
+
+\emph{See Section 8.4.1} for complete \verb|ClassifierBuilder.java| class.
+
+The class \verb|ClassifierValidator.java| handles validating and testing the existing classification models.
+To implement the ensemble classifier into this class, we will use the following, similar algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassifierValidator (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State testClassifier($i$, $testSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Test individual classifier
+            \State testClassifier($algorithm$, $testSet$, $modelPath$)
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+\emph{See Section 8.4.2} for complete \verb|ClassifierValidator.java| class.
+
+The class \verb|ClassPredictor.java| handles making the classification predictions on new data using existing classifier models.
+We can add the ensemble classification feature to this class with the following algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassPredictor (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \State list = new OutputFileList()
+            \For{algorithm $i=1\rightarrow4$}
+                \Comment Loop through all classifiers
+                \State makePredictions($i$, $inputData$, $modelsDirectory$)
+                \State list.add(ClassifierOutputFiles)
+                \Comment Add output filepaths to list
+            \EndFor
+            \State positiveList = new ClassificationsList()
+            \State negativeList = new ClassificationsList()
+            \Comment Create classification lists
+            \For{each OutputFile from list}
+                \If{OutputFile is .positive}
+                    \For{each line in OutputFile}
+                        \State positiveList.add(line)
+                        \Comment Add to +ve classifications
+                    \EndFor
+                \ElsIf{OutputFile is .negative}
+                    \For{each line in OutputFile}
+                        \State negativeList.add(line)
+                        \Comment Add to -ve classifications
+                    \EndFor
+                \EndIf
+            \EndFor
+            \For{each classification in positiveList}
+                \If{classification.occurrences $< 3$}
+                    \State negativeList.add(classification)
+                    \Comment cut-off at $< 3$ classifications
+                \Else
+                    \State positiveOutput(classification)
+                    \Comment Output classified as Pulsar
+                \EndIf
+            \EndFor
+            \For{each classification in negativeList}
+                \State negativeOutput(classification)
+                \Comment Output classified as non-Pulsar
+            \EndFor
+
+        \Else 
+            \State makePredictions($algorithm$)
+            \Comment Use individual classifier
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+The above algorithm preserves the individual classifiers' predictions and also makes an ensemble prediction based on all of the classifiers' predictions.
+According to \cite{tan}, it is common for ensemble machine learning classifiers to use a cut-off of three concurrent positive predictions in separate classifiers to make a positive ensemble classification.
+Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
+\emph{See Section 8.4.3} for the complete \verb|ClassPredictor.java| class.
+
+The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
+This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Section 8.4.4}.
+The complete source code to the \verb|PulsarClassifier| contains the following classes:
+
+\begin{lstlisting}[numbers=none]
+src/
+    main/
+        java/
+            com/jacobianmatthews/pulsarclassifier/
+                utils/
+                    Classification.java
+                    ClassificationList.java
+                    Classifiers.java
+                    Models.java
+                PulsarClassifier.java
+                ClassifierBuilder.java
+                ClassifierValidator.java
+                ClassPredictor.java
+
+            com/scienceguyrob/lotaasclassifier/
+                ...
+
+\end{lstlisting}
+
+Now that the source code for the package is complete, we can add the following lines to the \verb|pom.xml| file at the root of the project:
+
+\pagebreak
+\begin{lstlisting}[numbers=none, language=xml, title=pom.xml, basicstyle=\footnotesize\ttfamily]
+<project>
+    ...
+    <build>
+      <pluginManagement>
+        <plugins>
+          ...
+
+          <!-- Create a JAR containing the resources and dependencies -->
+          <plugin>
+            <groupId>org.apache.maven.plugins</groupId>
+            <artifactId>maven-assembly-plugin</artifactId>
+            <configuration>
+              <archive>
+                <manifest>
+                  <addClasspath>true</addClasspath>
+                  <mainClass>com.jacobianmatthews.pulsarclassifier.PulsarClassifier</mainClass>
+                </manifest>
+              </archive>
+              <descriptorRefs>
+                <descriptorRef>jar-with-dependencies</descriptorRef>
+              </descriptorRefs>
+            </configuration>
+            <executions>
+              <execution>
+                <phase>package</phase>
+                <goals>
+                  <goal>single</goal>
+                </goals>
+              </execution>
+            </executions>
+          </plugin>
+
+          ...
+        </plugins>
+      </pluginManagement>
+    </build>
+    ...
+</project>
+\end{lstlisting}
+
+This will instruct Maven to build a Java \verb|JAR| file containing the package and its WEKA library dependency. To build the package, we can run the following commands in the UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarClassifier
+$ mvn assembly:single
+\end{lstlisting}
+
+The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix 7.3}.
 
 \subsubsection{Evaluating PulsarClassifier}
+
+Now that we have successfully built \verb|PulsarClassifier|, we can evaluate its usage with the Murchison Widefield Array's (MWA) candidates. We begin by:
+\begin{enumerate}[label=\roman*.] 
+    \item deleting the previous \verb|output.positive| and \verb|output.negative| files from the \verb|PFD| candidates directory; and
+    \item deleting the previous \verb|model.m| file created by the \verb|LOTAASClassifier| software.
+\end{enumerate}
+
+We can now build the ensemble classification model with the training dataset created earlier, by running the following commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd target
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+Where the argument \verb|-m| now denotes the path to a directory to store the various classifier models.
+Now that we have all of the classification models created, we can use the ensemble classifier to predict the class of new candidates.
+Using the feature extracted candidates compiled from \emph{Section 2.2.2}, we can run the following command:
+
+\begin{lstlisting}[numbers=none]
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+\verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
+We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section 2.2.1} by running the commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarValidator/target
+$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_ensemble.positive ~/pulsars/data/pfd/output_ensemble.negative
+\end{lstlisting}
+
+The outputted validation statistics can then be compared to those created for the \verb|LOTAASClassifier| algorithms and an opinion can be formed in regards to the utility of \verb|PulsarClassifier| with the Murchison Widefield Array.
 
@@
 
-The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix 8.3}.
+The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix 7.1}.
 
-\subsection{Output from LOTAASClassifier with Murchison Widefield Array Data}
-\subsection{Output from PulsarClassifier Machine Learning Classification Tool}
+\subsection{Classification Results from the LOTAASClassifier Algorithms}
+
+\subsubsection{The J48 Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the J48 (C4.5 Decision Tree) algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 146
+True Positives: 131
+False Positives: 15
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 88
+True Negatives: 72
+False Negatives: 16
+\end{lstlisting}
+
+\subsubsection{The Multi-Layer Perceptron Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Multi-Layer Perceptron algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 125
+True Positives: 123
+False Positives: 2
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 109
+True Negatives: 85
+False Negatives: 24
+\end{lstlisting}
+
+\subsubsection{The Naïve Bayes Tester Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 119
+True Positives: 118
+False Positives: 1
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 115
+True Negatives: 86
+False Negatives: 29
+\end{lstlisting}
+
+\subsubsection{The Support Vector Machine Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 97
+True Positives: 97
+False Positives: 0
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 137
+True Negatives: 87
+False Negatives: 50
+\end{lstlisting}
+
+\subsection{Classification Results from the PulsarClassifier Ensemble Classifier}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the \verb|PulsarClassifier| ensemble classifier is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 165
+Pulsars Detected: 112
+True Positives: 112
+False Positives: 0
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 140
+True Negatives: 87
+False Negatives: 53
+\end{lstlisting}
 
@@
 % Results Discussion Section
-\section{Discussion}
-\subsection{How effective are the training datasets?}
+\section{Discussion and Conclusions}
+\subsection{How effective is the training dataset?}
 \subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
@@
 
-\pagebreak
-% FINAL CONCLUSTIONS SECTION
-\section{Conclusions}
-
 % RECOMMENDATIONS SECTION
 \section{Recommendations}
+
+For further development of the Machine Learning classifiers and strategies used in this project, I would recommend undertaking the following tasks:
+
+\begin{enumerate}
+    \item Investigate and fix the Python \verb|Traceback| Error produced by the software \verb|PulsarFeatureLab v1.3.2|:
+
+    During the usage of this feature extraction software, some \verb|PFD| candidate files would cause a \verb|Traceback| error to be produced, causing the feature extraction to fail for that particular candidate.
+In the \verb|PFD| datasets that I used, the only commonality between the failed feature extraction candidates was that the candidates were not pulsars - they were either examples of Radio Frequency Interference (RFI) or Noise.
+The result of these failures was that there was a smaller dataset to train the machine learning classifiers on, or a smaller dataset to make machine learning classification predictions on.
+
+    \item Build the Radio Frequency Interference (RFI) classification feature discussed by \cite{tan} into \verb|PulsarClassifier|:
+
+    According to \cite{tan}, by also including the classification category of RFI, the accuracy of the machine learning ensemble classifier was increased.
+The result of this feature would be three classifier output files: \verb|output.pulsars|, \verb|output.rfi|, and \verb|output.other|.
+
+    \item Use a more diverse Training Dataset:
+
+    Due to constraints on the available \verb|PFD| candidate data during this project, I was unable to use a large set of pulsar and non-pulsar candidates in the training dataset.
+By using a training dataset that is more diverse, the \verb|PulsarClassifier| will be more accurate in its predictions.
+\end{enumerate}
 
@@
 \section{Appendices}
-\subsection{Pulsar Feature Lab}
-\subsection{Pulsar Classifier}
+\subsection{Machine Learning Training Dataset}
+\lstinputlisting[title=trainingData.arff, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/trainingSet.arff}
 
 \pagebreak
-\subsection{Machine Learning Training Dataset}
-\lstinputlisting[title=trainingData.arff, basicstyle=\footnotesize\ttfamily, breaklines=true]{code/trainingSet.arff}
+\subsection{PulsarValidator}
+\subsubsection{PulsarValidator.java}
+\lstinputlisting[title=PulsarValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/PulsarValidator.java}
+
+\pagebreak
+\subsubsection{ValidationMode.java}
+\lstinputlisting[title=ValidationMode.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/ValidationMode.java}
+
+\pagebreak
+\subsubsection{utils/Statistic.java}
+\lstinputlisting[title=utils/Statistic.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/Statistic.java}
+
+\pagebreak
+\subsubsection{utils/StatisticList.java}
+\lstinputlisting[title=utils/StatisticList.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/StatisticList.java}
+
+\pagebreak
+\subsubsection{utils/Utilities.java}
+\lstinputlisting[title=utils/Utilities.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/Utilities.java}
+
+\pagebreak
+\subsection{PulsarClassifier}
+
+\subsubsection{PulsarClasifier.java}
+\lstinputlisting[title=PulsarClassifier.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/PulsarClassifier.java}
+
+\pagebreak
+\subsubsection{ClassifierBuilder.java}
+\lstinputlisting[title=ClassifierBuilder.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierBuilder.java}
+
+\pagebreak
+\subsubsection{ClassifierValidator.java}
+\lstinputlisting[title=ClassifierValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierValidator.java}
+
+\pagebreak
+\subsubsection{ClassPredictor.java}
+\lstinputlisting[title=ClassPredictor.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassPredictor.java}
+
+\pagebreak
+\subsubsection{utils/Classification.java}
+\lstinputlisting[title=utils/Classification.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true,framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Classification.java}
+
+\pagebreak
+\subsubsection{utils/ClassificationList.java}
+\lstinputlisting[title=utils/ClassificationList.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true,framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/ClassificationList.java}
+
+\pagebreak
+\subsubsection{utils/Classifiers.java}
+\lstinputlisting[title=utils/Classifiers.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Classifiers.java}
+
+\pagebreak
+\subsubsection{utils/Models.java}
+\lstinputlisting[title=utils/Models.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Models.java}
 

### 2020-05-30 code/jacobianmatthews/pulsarclassifier/ClassPredictor.java

@@ -1,0 +1,235 @@
+package com.jacobianmatthews.pulsarclassifier;
+
+import java.util.ArrayList;
+import java.util.List;
+import com.jacobianmatthews.pulsarclassifier.utils.Classification;
+import com.jacobianmatthews.pulsarclassifier.utils.ClassificationList;
+import com.jacobianmatthews.pulsarclassifier.utils.Classifiers;
+import com.jacobianmatthews.pulsarclassifier.utils.Models;
+import com.scienceguyrob.lotaasclassifier.classifiers.offline.J48Tester;
+import com.scienceguyrob.lotaasclassifier.classifiers.offline.MLPTester;
+import com.scienceguyrob.lotaasclassifier.classifiers.offline.NaiveBayesTester;
+import com.scienceguyrob.lotaasclassifier.classifiers.offline.SVMTester;
+import com.scienceguyrob.lotaasclassifier.io.Writer;
+import com.scienceguyrob.lotaasclassifier.utils.BasicLogger;
+import com.scienceguyrob.lotaasclassifier.wekawrappers.I_WekaTest;
+
+/**
+ * This class contains the methods and properties required to make predictions on data 
+ * to classify pulsars.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 24/05/20
+ */
+public class ClassPredictor extends com.scienceguyrob.lotaasclassifier.mvc.ClassPredictor {
+
+    // CONSTRUCTORS
+    public ClassPredictor(BasicLogger l, String n) { super(l, n); }
+    public ClassPredictor(String n){ super(n); }
+
+
+    public boolean predict(int algorithm, String predictPath, String modelsDir)
+    {
+        // Check if the ensemble classifier is being used
+        if ( algorithm == -1 )
+        {
+            // Get the prefix of the prediction output files (input file path without extension)
+            String fileName = predictPath.substring(0, predictPath.lastIndexOf("."));
+
+            // Create an array of the [output].positive and [output].negative files
+            List<String> positiveFiles = new ArrayList<String>();
+            List<String> negativeFiles = new ArrayList<String>();
+
+            // Create an index to count the number of classifiers successfully completing predictions
+            int predictCount = 0;
+
+            // Loop through the array of classifiers to make all predictions
+            for(int classifier: Classifiers.classifiers)
+            {
+                // Check the status of the classifier's predictions
+                if ( chooseClassifier(classifier, predictPath, modelsDir) )
+                {
[…]

### 2020-05-30 code/jacobianmatthews/pulsarclassifier/PulsarClassifier.java

@@ -1,0 +1,547 @@
+package com.jacobianmatthews.pulsarclassifier;
+
+import com.scienceguyrob.lotaasclassifier.classifiers.Classifiers;
+import com.scienceguyrob.lotaasclassifier.cli.CLI;
+import com.scienceguyrob.lotaasclassifier.cli.CLParameter;
+import com.scienceguyrob.lotaasclassifier.cli.ICLI;
+import com.scienceguyrob.lotaasclassifier.utils.BasicLogger;
+import com.scienceguyrob.lotaasclassifier.utils.Common;
+
+import java.net.URL;
+
+
+/**
+ * This class takes in command-line arguments and starts the PulsarClassifier
+ * program.
+ * 
+ * It is a derivative of the com.scienceguyrob.lotaasclassifier package.
+ *
+ * @author Jacob Ian Matthews & Rob Lyon
+ *
+ * @version 1.0, 22/5/2020
+ */
+public class PulsarClassifier {
+    /**
+     *
+     *	VARIABLES
+     *
+     */
+
+    /**
+     * Full path to the file containing training data.
+     */
+    private static String training_path = "";
+
+    /**
+     * Full path to the file (ARFF file) to be assigned classifier predictions.
+     */
+    private static String predict_path = "";
+
+    /**
+     * Full path to the classifier validation file (ARFF file).
+     */
+    private static String validate_path = "";
+
+    /**
+     * Full path to the file containing the classification model to use.
+     */
+    private static String model_path = "";
+
+    /**
+     * The algorithm to train/use to make predictions.
+     */
+    private static int algorithm = -1;
+
+    /**
+     * Logging flag, if true, verbose logging outputs will be written to standard out.
+     */
+    private static boolean verbose = false;
+
+    /**
+     * Training flag. If true the system will attempt to build a new classifier.
+     */
+    private static boolean train = false;
+
+    /**
+     * Prediction flag. If true the system will attempt to classify data.
+     */
+    private static boolean predict = false;
+
+    /**
+     * Validation flag. If true, the system will attempt to validate the classifiers performance.
+     */
+    private static boolean validate = false;
+
+    /**
+     * The working directory for this code.
+     */
+    private static URL workingDir = PulsarClassifier.class.getProtectionDomain().getCodeSource().getLocation();
+
+    /**
+     * The object used to output debug/logging information.
+     */
+    private static BasicLogger log = new BasicLogger(verbose,workingDir.getFile().replace(".jar",".log"));
+
+    //*****************************************
+    //*****************************************
[…]

### 2020-05-30 code/jacobianmatthews/pulsarclassifier/utils/ClassificationList.java

@@ -1,0 +1,186 @@
+package com.jacobianmatthews.pulsarclassifier.utils;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import com.scienceguyrob.lotaasclassifier.io.Reader;
+
+/**
+ * This class creates a list with a key-value pairing system to use inside a
+ * list. It is used as a part of ClassPredictor.java to keep track of the number
+ * of occurrences of positive and negative pulsar classifications.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 24/05/20
+ * 
+ */
+public class ClassificationList 
+{
+    
+    /**
+     * Variables
+     */
+    public List<Classification> list;
+
+    /**
+     * Constructor
+     */
+    public ClassificationList()
+    {
+        // Create the list
+        this.list = new ArrayList<Classification>();
+    }
+
+    /**
+     * 
+     * @param index index in the list of the item to retrieve
+     * @return the Key-Value pair at the list index
+     */
+    public Classification get(int index)
+    {
+        // Return the list item 
+        return list.get(index);
+    }
+
+    public List<Classification> getList()
+    {
+        return this.list;
+    }
+
+    /**
+     * 
+     * @return the number of items in the list
+     */
+    public int size()
+    {
+        // Get the size of the list
+        return list.size();
+    }
+
+   
+    public void add(String key, int value)
+    {
+        // Create a new entry and add it to the list
+        list.add(new Classification(key, value));
+
+    }
+
+    /**
+     * Get the value of a key-value pair inside the list, found by its key.
+     * @param key String with the key of the pair
+     * @return Integer value of the pair or 0 if it doesn't exist.
+     */
+    public int getValueByKey(String key)
+    {
+
+        // Loop through the list until the pair is found
+        for(Classification item: this.list)
+        {
+            // Check the string against the provided string
+            if( item.getKey().equals(key) )
+            {
+                // Found the classification item, get its value
+                return item.getValue();
+            }
+        }
+
+        // Return 0 since it wasn't found
+        return 0;
+
+    }
+
+    /**
+     * Sets the value of a key-value pair inside the list, by its key.
+     * @param key String key of the pair.
+     */
+    public void setValueByKey(String key, int value)
+    {
+        // Loop through the list until the key-value pair is found
+        for(Classification item: this.list)
+        {
+            // Compare the string keys
+            if ( item.getKey().equals(key) )
+            {
+                // Found the pair, updated the value
[…]

### 2020-05-30 code/jacobianmatthews/pulsarvalidator/PulsarValidator.java

@@ -1,0 +1,151 @@
+package com.jacobianmatthews.pulsarvalidator;
+
+import java.io.IOException;
+
+/**
+ * This program is a validator for the machine learning software
+ * PulsarClassifier.
+ * 
+ * This program will generate a list of candidate filenames from an output file
+ * of PulsarFeatureLab. It will then be possible to filter the list of known
+ * pulsars in the original dataset to the pulsars that had successful feature
+ * extraction. Finally, the program can compare the list of known pulsars in the
+ * dataset to the pulsars classified in the classifier, and produce comparison
+ * statistics.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 28/05/2020
+ */
+public class PulsarValidator {
+
+    /**
+     * 
+     * VARIABLES
+     * 
+     */
+
+    // Pulsar list mode
+    private static boolean list = false;
+
+    // Pulsar classification output validation mode
+    private static boolean validation = false;
+
+    // String containaing the path to the PulsarFeatureLab output file
+    private static String pflOutput;
+
+    // String containing the path to the list of pulsars
+    private static String pulsarList;
+
+    // String containing the path to the positive classifier output
+    private static String positiveClassifier;
+
+    // String containing the path to the negative classifier output
+    private static String negativeClassifier;
+
+    public static void main(String[] args) throws IOException {
+        // Get the input arguments
+        getCliVariables(args);
+
+        // Check to see which flag has been given
+        if (list) {
+            // LIST MODE CHOSEN
+            // Print a message
+            System.out.println("Pulsar list generation mode chosen.\n");
+
+            // Create a list mode instance
+            System.out.println("This feature is under development. Exiting program.");
+            System.exit(0);
+
+        } else if (validation) {
+
+            // VALIDATION MODE CHOSEN
+            // Print a message
+            System.out.println("\nPulsar classifier validation mode chosen.");
+
+            // Print the location of the pulsar list
+            System.out.println("\nPulsar list location: "+pulsarList);
+
+            // Print the location of the positive output file
+            System.out.println("Classifier positive output location: "+positiveClassifier);
+
+            // Print the location of the positive output file
+            System.out.println("Classifier negative output location: "+negativeClassifier);
+
+            // Create the validation mode instance
+            ValidationMode validationMode = new ValidationMode(pulsarList, positiveClassifier, negativeClassifier);
+
+            // Get the output string
+            String output = validationMode.validate();
+
+            // Output the string and then exit the program
[…]

### 2020-05-30 code/jacobianmatthews/pulsarvalidator/ValidationMode.java

@@ -1,0 +1,258 @@
+package com.jacobianmatthews.pulsarvalidator;
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Paths;
+import java.util.ArrayList;
+import java.util.List;
+
+import com.jacobianmatthews.pulsarvalidator.utils.StatisticList;
+import com.jacobianmatthews.pulsarvalidator.utils.Utilities;
+
+/**
+ * This class contains the Pulsar Classifier validation mode of the program. It
+ * will compare the output files of the Pulsar Classifier to the true list of
+ * pulsars and output statistics.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 29/05/2020
+ */
+public class ValidationMode {
+
+    /** VARIABLES */
+    private String positiveOutputPath;
+
+    private String negativeOutputPath;
+
+    private List<String> pulsars;
+
+    /** CONSTRUCTOR */
+    /**
+     * Instantiates the Validation mode.
+     * 
+     * @param pulsarListPath     A string containing the path to the list of pulsars
+     *                           in the data set.
+     * @param postiveOutputPath  A string containing the path to the positive output
+     *                           file of the classifier.
+     * @param negativeOutputPath A string containing the path to the negative output
+     *                           file of the classifier.
+     * @throws IOException
+     */
+    public ValidationMode(String pulsarListPath, String positiveOutputPath, String negativeOutputPath)
+            throws IOException {
+
+        // Assign the variables
+        this.positiveOutputPath = positiveOutputPath;
+        this.negativeOutputPath = negativeOutputPath;
+
+        // Validate the filepaths
+        if (!Utilities.isFile(pulsarListPath)) {
+            // Print an error and end the program
+            System.out.println("The path given to the pulsar list is not valid.\nExiting program.");
+            System.exit(0);
+        }
+
+        if (!Utilities.isFile(positiveOutputPath)) {
+            // Print an error and end the program
+            System.out.println("The path given to the positive classifier output is not valid.\nExiting program.");
+            System.exit(0);
+        }
+
+        if (!Utilities.isFile(negativeOutputPath)) {
+            // Print an error and end the program
+            System.out.println("The path given to the negative classifier output is not valid.\nExiting program.");
+            System.exit(0);
+        }
+
+        // Get the list of pulsars
+        this.pulsars = Files.readAllLines(Paths.get(pulsarListPath));
+
+    };
+
+    /**
[…]

### 2020-05-30 code/jacobianmatthews/pulsarvalidator/utils/Statistic.java

@@ -1,0 +1,45 @@
+package com.jacobianmatthews.pulsarvalidator.utils;
+
+/**
+ * This is a data object to hold a statistic for the classifier.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 29/05/2020
+ */
+public class Statistic {
+
+    /** VARIABLES */
+    private String name;
+    private int value;
+
+    /** CONSTRUCTOR */
+    public Statistic(String name, int value) {
+
+        // Get the variables
+        this.name = name;
+        this.value = value;
+        
+    }
+
+    /** GETTERS AND SETTERS */
+    public void setValue(int value)
+    {
+        this.value = value;
+    }
+
+    public int getValue(){
+
+        return this.value;
+    }
+
+    public void setName(String name)
+    {
+        this.name = name;
+    }
+
+    public String getName()
+    {
+        return this.name;
+    }
+    
+}

### 2020-05-30 code/jacobianmatthews/pulsarvalidator/utils/StatisticList.java

@@ -1,0 +1,60 @@
+package com.jacobianmatthews.pulsarvalidator.utils;
+
+import java.util.ArrayList;
+import java.util.List;
+
+/**
+ * A list to hold the classifier's statistics.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 29/05/2020
+ */
+public class StatisticList {
+
+    /** VARIABLES */
+    private List<Statistic> list;
+
+    /** CONSTRUCTOR */
+    public StatisticList() {
+
+        // Create the list
+        this.list = new ArrayList<Statistic>();
+
+    }
+
+    /**
+     * 
+     * @param name
+     * @param value
+     */
+    public void add(String name, int value)
+    {  
+        // Create a statistic
+        Statistic stat = new Statistic(name, value);
+
+        // Add it to the list
+        this.list.add(stat);
+    }
+
+    /**
+     * Get the value of a statistic by its name
+     * @param name String containing the name of the statistic
+     * @return integer value of statistic
+     */
+    public int getValueByName(String name)
+    {
+        // Loop through the list
+        for(Statistic stat: this.list)
+        {
+            if( stat.getName().equals(name) ){
+
+                // Return the value
+                return stat.getValue();
+            }
+        }
+
+        // Couldn't find it, return 0
+        return 0;
+    }
+
+}

### 2020-05-30 code/jacobianmatthews/pulsarvalidator/utils/Utilities.java

@@ -1,0 +1,44 @@
+package com.jacobianmatthews.pulsarvalidator.utils;
+
+import java.io.File;
+
+/**
+ * This class contains the common utility functions across the program.
+ * 
+ * @author Jacob Ian Matthews
+ * @version 1.0, 29/05/2020
+ */
+public class Utilities {
+
+    /** CONSTRUCTOR */
+    public Utilities(){
+        // Empty
+    }
+    
+    /**
+     * This method validates that a file exists.
+     * @param path A string containing the path to a file.
+     * @return True if it is a valid, existing file.
+     */
+    public static boolean isFile(String path)
+    {
+        // Trim the whitespace
+        String trimmed = path.trim();
+
+        // Create the file
+        File file = new File(trimmed);
+
+        // Validate the file
+        if(file.isFile()){
+            
+            // Return true
+            return true;
+        } else {
+
+            // Return false;
+            return false;
+
+        }
+
+    }
+}

### 2020-05-30 Draft.tex
Analyses

@@
 \usepackage{enumitem}
+\usepackage{framed}
 \usepackage{graphicx}
@@
 % Results Section
-\section{Results and Outputs}
+\section{Results and Analyses}
 \subsection{Machine Learning Training Dataset}
@@
 
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N_p} = \frac{131}{147} =  0.8911 = 89.11\%,$$
+
+where $N_p$ is the number of pulsars in the testing dataset and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{72}{87} = 0.8275 = 82.75\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
 \subsubsection{The Multi-Layer Perceptron Algorithm}
@@
 \end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{123}{147} =  0.8367 = 83.67\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{85}{87} = 0.9770 = 97.70\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
 
@@
 
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{118}{147} =  0.8027 = 80.27\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{86}{87} = 0.9885 = 98.85\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
 \subsubsection{The Support Vector Machine Algorithm}
@@
 
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{97}{147} =  0.6598 = 65.98\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
 \subsection{Classification Results from the PulsarClassifier Ensemble Classifier}
@@
 \begin{lstlisting}[numbers=none]
-Number of Pulsars: 165
+Number of Pulsars: 147
 Pulsars Detected: 112
@@
 Number of Non-Pulsars: 87
-Non-Pulsars Detected: 140
+Non-Pulsars Detected: 122
 True Negatives: 87
-False Negatives: 53
+False Negatives: 35
 \end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{112}{147} =  0.7619 = 76.19\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsection{Combined Analyses}
+
+A table containing the pulsar and non-pulsar classification success rates of all algorithms and the ensemble classifier can be found below:
+
+\begin{table}[H]
+    \centering
+
+    \caption{Success Rates of Each Pulsar Classifier}
+
+    \begin{framed}
+        \begin{tabular}{l c c c}
+            Classifier & $R_p$ & $R_{np}$ & $Combined$ \\
+            \hline
+            \hline
+            LOTAASClassifier &  &  & \\
+            \hline
+            J48 & 89.11\% & 82.75\% & 85.93\% \\
+            MLP & 83.67\% & 97.70\% & 90.69\% \\
+            NB & 80.27\% & 98.85\% & 89.56\%\\
+            SVM & 65.98\% & 100.00\% & 82.99\% \\
+            \hline
+            PulsarClassifier &  &  & \\
+            \hline
+            Ensemble & 76.19\% & 100.00\% & 88.10\% \\
+        \end{tabular}
+    \end{framed}
+    \label{tab:analyses}
+\end{table}
 
@@
 \section{Discussion and Conclusions}
-\subsection{How effective is the training dataset?}
+\subsection{How effective is the chosen training dataset?}
 \subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
@@
 
+\pagebreak
 % RECOMMENDATIONS SECTION
@@
 
-    \item Build the Radio Frequency Interference (RFI) classification feature discussed by \cite{tan} into \verb|PulsarClassifier|:
+    \item Build the Radio Frequency Interference (RFI) classification feature discussed by \textcite{tan} into \verb|PulsarClassifier|:
 
-    According to \cite{tan}, by also including the classification category of RFI, the accuracy of the machine learning ensemble classifier was increased.
+    According to \textcite{tan}, by also including the classification category of RFI, the accuracy of the machine learning ensemble classifier was increased.
 The result of this feature would be three classifier output files: \verb|output.pulsars|, \verb|output.rfi|, and \verb|output.other|.

### 2020-05-30 code/jacobianmatthews/pulsarclassifier/ClassPredictor.java

@@ -130,11 +130,16 @@ public class ClassPredictor extends com.scienceguyrob.lotaasclassifier.mvc.Class
                         // Get the key of the classification
                         String key = negative.getKey();
 
-                        // Append it to the output file
-                        if( !Writer.append(ensembleNegative, key+"\n") )
+                        // Make sure that it isn't already in the positive or negative output files
+                        if( !Reader.checkStringIsInFile(ensembleNegative, key) && !Reader.checkStringIsInFile(ensemblePositive, key))
                         {
-                            // Log the error 
-                            log.sout("Couldn't add "+key+" to the negative ensemble classifier output file.", true);
+                            // Append it to the output file
+                            if( !Writer.append(ensembleNegative, key+"\n") )
+                            {
+                                // Log the error 
+                                log.sout("Couldn't add "+key+" to the negative ensemble classifier output file.", true);
+
+                            }
 
                         }
                     }

### 2020-06-03 Draft.tex
Table
appendices

@@
 \usepackage{graphicx}
+\usepackage[title,toc,page]{appendix}
 
@@
 % Create the Title 
-\title{Finding New Pulsars Using Machine Learning}
-\author{Jacob Ian Matthews \\ \\ Draft}
+\title{\large{Curtin University} \\ \large{Curtin Institute of Radio Astronomy} \\ \large{Physics Project 1} \\ \vspace*{20px} \textbf{\LARGE{Finding New Pulsars Using Machine Learning}}\vspace*{10px}}
+\author{\vspace*{20px} Jacob Ian Matthews \\ \\ Draft}
 
@@
 
-    \section*{Abstract}
+    \vspace*{20px}
+
+    \begin{abstract}
+
+    \end{abstract}
 
@@
     \item Create a training dataset for a Machine Learning algorithm to find pulsars in data obtained by the Murchison Widefield Array (MWA); and
-    \item Evaluate the utility of the Machine Learning algorithm used by the LOFAR Telescope for the Murchison Widefield Array, and adjust the algorithm as necessary to achieve optimum pulsar candidate generation.
+    \item Evaluate the utility of the Machine Learning algorithms used by the LOFAR Telescope for the Murchison Widefield Array, and adjust the algorithms as necessary to achieve optimum pulsar candidate classification.
 \end{enumerate}
@@
 
-In this report, I will first explain in \emph{Section 1.3} how Pulsars, Radio Astronomy, and Machine learning work, and then explain what has been dubbed the ``Candidate Selection Problem" \autocite{lyon} and why Machine Learning is necessary in completing future pulsar surveys.
-
-In \emph{Section 2} I discuss the methods undertook in: (i) developing the machine learning training dataset for the Murchison Widefield Array algorithm, and (ii) evaluating the machine learning algorithm used by the LOFAR surveys for use with the Murchison Widefield Array.
-
-In \emph{Section 3} I analyse the results and findings obtained by the methods described in \emph{Section 2}, and in \emph{Section 4} I will discuss (i) the efficacy of the training datasets, and (ii) the usefulness of the LOFAR machine learning algorithm with the Murchison Widefield Array and why changes were made to the algorithm.
-
-This report will end with my final conclusions on the use of machine learning in discovering new pulsars (\emph{Section 5}), and my recommendations to future researchers undertaking a similar project (\emph{Section 6}).
+In this report, I will first explain in \emph{Section 1.3} how Pulsars, Radio Astronomy, and Machine learning work, and then explain the ``Candidate Selection Problem" \autocite{lyon} and why Machine Learning is necessary in completing future pulsar surveys.
+
+In \emph{Section 2}, I discuss the methods undertaken in: (i) developing the machine learning training dataset for the Murchison Widefield Array, (ii) developing software to validate the output of machine learning classifiers, (iii) evaluating the machine learning algorithms used by the LOFAR surveys for use with the Murchison Widefield Array, and (iv) developing an ensemble machine learning classifier to be used with the Murchison Widefield Array and other radio telescopes.
+
+In \emph{Section 3}, I analyse the results and findings obtained by the methods described in \emph{Section 2}, and in \emph{Section 4} I will discuss (i) the current pulsar classification methods used at the Curtin Institute of Radio Astronomy, (ii) the efficacy of the machine learning classifiers and training dataset produced in this report, and (iii) my concluding remarks about the utility of the machine learning classifiers with the Murchison Widefield Array.
+
+This report will conclude with my recommendations for areas of further development in \emph{Section 5}, and the detailed methodologies in creating the results of this project, and entirety of the source code created undertaking this project, in the \emph{Appendices}.
 
@@
 
-To answer the question of "what is a pulsar?" we must first investigate the evolution and death of stars.
+\subsubsection{Pulsars}
+
+To answer the question of ``what is a pulsar?" we must first investigate the evolution and death of stars.
 
@@
 Where candidate features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile.
-See \emph{Appendix 2A} for formulae to calculate each feature.
 
@@
 
-The Python software tool \verb|PulsarFeatureLab| can be used to consume pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
-
-To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software are unaffected by the host operating system, a containerised virtual operating system can be created using the free software Docker (\verb|https://docker.com|).
+The Python software tool \verb|PulsarFeatureLab| can be used to process pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
+
+To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software are unaffected by the host operating system, a containerised virtual operating system was created using the free software Docker (\verb|https://docker.com|).
 
@@
 \subsubsection{Creating a Pulsar Classifier Output Validation Tool}
-
+\label{sec:methodvalidate}
 In order to accurately evaluate and test the predictions made by the \verb|LOTAASClassifier| tool, we must create a program that will automate the process of checking the outputs of the classifier against the known list of pulsars.
@@
 We can then use a simple conditional statement after this function is ran to check if the \verb|Boolean ValidationMode| has been set to \verb|true|, to determine whether to continue the validation.
-The complete Java class \verb|PulsarValidator.java| can be seen in \emph{Appendix 7.2.1}.
+The complete Java class \verb|PulsarValidator.java| can be seen in \emph{Appendix \ref{sec:pulsarvalidator}.1}.
 
@@
 \subsubsection{Creating the PulsarClassifier Ensemble Classification Tool}
-
+\label{sec:methodensemble}
 According to \cite{tan}, using Machine Learning algorithms in ensemble to make pulsar classifications increases the accuracy of classifications, classifying pulsars that were often misclassified such as wide-pulse pulsars.
@@
 
-\emph{See Section 8.4.1} for complete \verb|ClassifierBuilder.java| class.
+See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
 
@@
 
-\emph{See Section 8.4.2} for complete \verb|ClassifierValidator.java| class.
+See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
 
@@
 Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
-\emph{See Section 8.4.3} for the complete \verb|ClassPredictor.java| class.
+See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
 
 The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
-This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Section 8.4.4}.
+This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
 The complete source code to the \verb|PulsarClassifier| contains the following classes:
@@
 
-The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix 7.3}.
+The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{sec:pulsarclassifier}}.
 
@@
 \verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
-We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section 2.2.1} by running the commands:
+We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
 
@@
 
-The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix 7.1}.
+The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix \ref{sec:training}}.
 
@@
         \end{tabular}
+
+        \vspace{5px}
+        $R_p$: Success rate of pulsar classification.\\
+        $R_{np}$: Success rate of non-pulsar classification. \\
     \end{framed}
@@
 \section{Discussion and Conclusions}
-\subsection{How effective is the chosen training dataset?}
 \subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
-\subsection{Why did/didn't the LOFAR Machine Learning Algorithm work with the MWA?}
-\subsection{What changes to the algorithm were necessary for it to successfully classify Pulsars from the MWA?}
+
+A pulsar classification pipeline can be defined as the process undertaken to classify a candidate as a pulsar \autocite{swainston}.
+The current pipeline at the Curtin Institute of Radio Astronomy (CIRA) for pulsar classification is as follows:
+\begin{enumerate}[label=\roman*.]
+    \item Generate pulsar candidates through the SMART (Southern-sky MWA Rapid Two-metre) survey;
+    \item Extract machine learning features from the pulsar candidates using \\\verb|PulsarFeatureLab|;
+    \item Use the LOFAR Tied-Array All-Sky machine learning pulsar classifier, \verb|LOTAASClassifier|, to to eliminate a large number of pulsar candidates; and
+    \item Manually inspect the remaining pulsar candidates to confirm pulsar discovery.
+\end{enumerate}
+\autocite{swainston}. While the classification pipeline itself appears to be optimal, I have identified a few issues with the previous attempts at CIRA in using the machine learning classifier.
+
+The first issue revolves around the use of mislabelled and incomplete software.
+In the research completed by \textcite{tan}, the original \\\verb|LOTAASClassifier|, created by \textcite{lyon}, was upgraded to include two major new features: (i) ensemble classification, and (ii) radio frequency interference (RFI) classification.
+The machine learning feature set was also expanded from 8 features in \textcite{lyon} to 20 features in \textcite{tan}, greatly improving the accuracy of classification.
+Upon analysis of the source code of \verb|LOTAASClassifier|, it appears that the two new classification features were not released publicly, despite the software being labelled as \verb|LOTAASClassifier v2.0| in its main Java class, the same name referenced by \textcite{tan}.
+Despite this, the new, expanded set of machine learning features was released with \verb|PulsarFeatureLab Version 1.3.2|.
+This created a mismatch between the feature extraction software and the machine learning classifier, which leads to the next issue in the CIRA pipeline: the training dataset.
+
+In the pipeline provided by \textcite{swainston}, it appears that CIRA has been attempting to use the training dataset generated for the LOFAR Tied-Array All-Sky Survey included with the \verb|LOTAASClassifier| software, for pulsar candidates generated in the SMART survey.
+In itself, this may not present issues, however due to the unknown mismatch in the machine learning software, an issue of feature dimensions occurs.
+The included training dataset creates a classification model with the original 8 machine learning features, therefore any predictions on new candidates would require the same 8 machine learning features to have been extracted prior to classification.
+Due to the mislabelled software, CIRA has been extracting the set of 20 features from pulsar candidates and attempting to make classifications against a set of 8 features, preventing classifications from occurring in \verb|LOTAASClassifier| due to a mismatch in dimensions.
+This issue can be fixed by creating a training dataset with the same set of extracted features as will be present in the candidates for classification.
+
+The final issue arising in the CIRA pipeline also spouts from the mislabelling of the \verb|LOTAASClassifier| software.
+The CIRA pipeline expects that the ensemble classifier created in the upgraded software from \textcite{tan} will be used.
+Without the latest version of \verb|LOTAASClassifier| having been released, the CIRA pipeline defaults to using the J48 machine learning classification algorithm.
+As seen in Table \ref{tab:analyses} from \emph{Section 3.4}, the J48 algorithm does not appear to be optimal in combined pulsar and non-pulsar classification.
+To fix this issue, an ensemble machine learning classifier was created in \emph{Section 2.2.4} to replace the \verb|LOTAASClassifier| software.
+
+\subsection{Evaluating the Training Dataset and Machine Learning Classifiers}
+
+An evaluation of the machine learning classifiers: \verb|LOTAASClassifier| and its algorithms, and \verb|PulsarClassfier|, will in its nature be subject to the quality of the training dataset used.
+By inspecting the data produced in \emph{Section 3.2}, we can see the success rates of pulsar and non-pulsar classification, which are defined as the ratio of the number of true positive (true negative) classifications with the number of pulsars (non-pulsars).
+The success rates of each classifier are then compiled into Table \ref{tab:analyses}.
+Another metric, the combined success rate, is also introduced as the mean of the two success rates.
+The combined success rate can be used to rank the total accuracy of the classifiers, however this metric does not contain ample information.
+The classifiers can thus be ranked in order of highest total accuracy:
+
+\begin{enumerate}
+    \item Multi-Layered Perceptron (90.69\%)
+    \item Naïve Bayes Test (89.56\%)
+    \item Ensemble Classifier (88.10\%)
+    \item J48 (C4.5 Decision Tree) (85.93\%)
+    \item Support Vector Machine (82.99\%)
+\end{enumerate}
+
+Despite being ranked third in combined success rates, the \verb|PulsarClassifier|'s Ensemble Classifier was only one of two classifiers that correctly classified all examples of noise and radio frequency interference as \emph{non-pulsar}, the other successful classifier being the Support Vector Machine.
+As a result of this, there were no false positive classifications completed by the Ensemble classifier, i.e.
+everything classified as a pulsar actually was a pulsar.
+The Ensemble Classifier was let down by misclassifying 35 pulsars, having the second-lowest success rate of pulsar classification - the lowest being the Support Vector Machine which misclassified 50 pulsars, and the highest being the J48 Classifier having misclassified only 16 pulsars.
+
+For the use case of classifying pulsar candidates generated from the Murchison Widefield Array, the most important metric to be considered when evaluating a machine learning classifier is the pulsar classification success rate.
+It is more important to not miss the classification of a pulsar and less important if a non-pulsar is classified as a pulsar.
+For this reason, the objective is to maximise the rate of true positive classifications and minimise the rate of false negative classifications.
+
+The training dataset created in this project contained 11 examples of pulsars and 12 examples of noise and radio frequency interference (RFI).
+While the training dataset appeared to have a satisfactory variety of noise and RFI, contributing to the ensemble classifier's perfect rate of non-pulsar classification, the set of pulsars appeared to be unsatisfactory.
+In order to improve the success rate of pulsar classification (positive success rate) in the ensemble classifier, we must use a modified training dataset that will improve the positive success rate in the worst performing individual classifiers: the Support Vector Machine (65.98\%), and the Naïve Bayes Test (80.27\%), whilst maintaining the higher positive success rates of the other classifiers.
+By doing so, more pulsars will survive the ensemble classifier's individual classification criteria of 3 or more, and thus the positive success rate will improve.
+This modification to the training dataset could involve changing the included set of pulsars to include a subset of pulsars of ordinary appearing features, and the remaining subset of pulsars should exhibit unusual or difficult to discern features.
+
+In conclusion, I believe that the machine learning classifiers in the \\\verb|LOTAASClassifier| software, particularly used in ensemble such as with the \verb|PulsarClassifier| software created for this project, are of great utility for current and future Murchison Widefield Array pulsar surveys.
+As discussed in \textcite{lyon}, the number of pulsar candidates generated in pulsar surveys stands to grow exponentially beyond the economical capacity of data storage and viability of manual examination.
+This problem requires a solution to filter out the non-pulsars from the group of candidates to maximise the discovery of pulsars, and I believe that the \verb|PulsarClassifier| software is another step forward in solving the problem.
+While the training dataset does require further development to maximise the success of the Ensemble Classifier, the Machine Learning techniques themselves proved to be extremely valuable in pulsar classification.
 
@@
 \begin{enumerate}
-    \item Investigate and fix the Python \verb|Traceback| Error produced by the software \verb|PulsarFeatureLab v1.3.2|:
+    \item Investigate and fix the Python \verb|Traceback Error| produced by the software \verb|PulsarFeatureLab v1.3.2|:
 
     During the usage of this feature extraction software, some \verb|PFD| candidate files would cause a \verb|Traceback| error to be produced, causing the feature extraction to fail for that particular candidate.
-In the \verb|PFD| datasets that I used, the only commonality between the failed feature extraction candidates was that the candidates were not pulsars - they were either examples of Radio Frequency Interference (RFI) or Noise.
-The result of these failures was that there was a smaller dataset to train the machine learning classifiers on, or a smaller dataset to make machine learning classification predictions on.
+The result of these failures was that there was a smaller dataset to train the machine learning classifiers on, and a smaller dataset to make machine learning classification predictions on.
 
@@
 % APPENDICES SECTION
-\section{Appendices}
+\begin{appendices}
+
+    \section{Methods}
+    \begin{subappendices}
+        \subsection{Feature Extraction with PulsarFeatureLab}
+
+        \subsection{Using PulsarValidator}
+
+    \end{subappendices}
+
+    \section{Results}
     \subsection{Machine Learning Training Dataset}
-\lstinputlisting[title=trainingData.arff, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/trainingSet.arff}
-
-\pagebreak
-\subsection{PulsarValidator}
-\subsubsection{PulsarValidator.java}
+    \label{sec:training}
+    \lstinputlisting[title=trainingData.arff, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em, literate={,}{{,\allowbreak}}1]{code/trainingSet.arff}
+
+    \pagebreak
+    \section{Pulsar Validator}
+    \begin{subappendices}
+        \label{sec:pulsarvalidator} 
+        \subsection{PulsarValidator.java}
         \lstinputlisting[title=PulsarValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/PulsarValidator.java}
@@
         \pagebreak
-\subsubsection{ValidationMode.java}
+        \subsection{ValidationMode.java}
         \lstinputlisting[title=ValidationMode.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/ValidationMode.java}
@@
         \pagebreak
-\subsubsection{utils/Statistic.java}
+        \subsection{utils/Statistic.java}
         \lstinputlisting[title=utils/Statistic.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/Statistic.java}
@@
         \pagebreak
-\subsubsection{utils/StatisticList.java}
+        \subsection{utils/StatisticList.java}
         \lstinputlisting[title=utils/StatisticList.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/StatisticList.java}
@@
         \pagebreak
-\subsubsection{utils/Utilities.java}
+        \subsection{utils/Utilities.java}
         \lstinputlisting[title=utils/Utilities.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/utils/Utilities.java}
 
-\pagebreak
-\subsection{PulsarClassifier}
-
-\subsubsection{PulsarClasifier.java}
+    \end{subappendices}
+
+    \pagebreak
+    \section{Pulsar Classifier}
+    \begin{subappendices}
+        \label{sec:pulsarclassifier}
+        \subsection{PulsarClassifier.java}
         \lstinputlisting[title=PulsarClassifier.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/PulsarClassifier.java}
@@
         \pagebreak
-\subsubsection{ClassifierBuilder.java}
+        \subsection{ClassifierBuilder.java}
         \lstinputlisting[title=ClassifierBuilder.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierBuilder.java}
@@
         \pagebreak
-\subsubsection{ClassifierValidator.java}
+        \subsection{ClassifierValidator.java}
         \lstinputlisting[title=ClassifierValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierValidator.java}
@@
         \pagebreak
-\subsubsection{ClassPredictor.java}
+        \subsection{ClassPredictor.java}
         \lstinputlisting[title=ClassPredictor.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassPredictor.java}
@@
         \pagebreak
-\subsubsection{utils/Classification.java}
+        \subsection{utils/Classification.java}
         \lstinputlisting[title=utils/Classification.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true,framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Classification.java}
@@
         \pagebreak
-\subsubsection{utils/ClassificationList.java}
+        \subsection{utils/ClassificationList.java}
         \lstinputlisting[title=utils/ClassificationList.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true,framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/ClassificationList.java}
@@
         \pagebreak
-\subsubsection{utils/Classifiers.java}
+        \subsection{utils/Classifiers.java}
         \lstinputlisting[title=utils/Classifiers.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Classifiers.java}
@@
         \pagebreak
-\subsubsection{utils/Models.java}
+        \subsection{utils/Models.java}
         \lstinputlisting[title=utils/Models.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/utils/Models.java}
+    \end{subappendices}
+\end{appendices}
 

### 2020-06-03 Draft.tex
Abstract

@@
     \begin{abstract}
+
+        As radio telescope technology improves, the number of candidate detections to be classified as pulsar or non-pulsar during pulsar surveys increases to the point that it becomes infeasible to classify them manually, a state of affairs known as the "pulsar candidate selection problem".
+To solve this problem, machine learning (ML) techniques are used to filter out the non-pulsar candidates in surveys, reducing the number of candidates requiring human evaluation to a manageable number.
+Here, we adapt an ML solution developed for the LOFAR Tied-Array All-Sky Survey (LOTAAS) for the Southern-sky Murchison Widefield Array Rapid Two-metre (SMART) survey.
+A group of 147 pulsar and 87 non-pulsar candidates generated by the SMART survey were used to test the LOTAAS ML classifiers trained on a set of 12 pulsar and 13 non-pulsar SMART survey candidates.
+The classifiers were found, on average, to make accurate pulsar and non-pulsar classifications on SMART survey candidates 87.3\% of the time, compared to the 97.1\% success rate obtained by \textcite{lyon}.
+Using the machine learning classifiers in ensemble with a selection criteria of three separate positive classifications increased the success rate of non-pulsar classification by 5.2\% (making 0 False Positive classifications), however it decreased the success rate of pulsar classification by 3.5\%.
+The ensemble machine learning classifier can be further improved by increasing the diversity of pulsars within the machine learning training dataset.
 

### 2020-06-03 Draft.tex
methods

@@
     \maketitle
+    \thispagestyle{empty}
 
@@
 
-        As radio telescope technology improves, the number of candidate detections to be classified as pulsar or non-pulsar during pulsar surveys increases to the point that it becomes infeasible to classify them manually, a state of affairs known as the "pulsar candidate selection problem".
+        As radio telescope technology improves, the number of candidate detections to be classified as pulsar or non-pulsar during pulsar surveys increases to the point that it becomes infeasible to classify them manually, a state of affairs known as the ``pulsar candidate selection problem".
 To solve this problem, machine learning (ML) techniques are used to filter out the non-pulsar candidates in surveys, reducing the number of candidates requiring human evaluation to a manageable number.
@@
 To maximise the accuracy of the machine learning algorithm, the input data (including the training dataset) must be composed of a common group of features that can be determined for each candidate that maximises the differences between a pulsar and a non-pulsar.
-The candidate features used by \smartcite{tan} to maximise the differences between pulsar and non-pulsar candidates are:
+The candidate features used by \textcite{tan} to maximise the differences between pulsar and non-pulsar candidates are:
 
@@
 
-Where candidate features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and from the (4) correlation coefficients between each sub-integration and the integrated pulsar profile.
-
-To extract the 20 above features from each classification candidate, we can use the software 
-\verb|PulsarFeatureLab| \autocite{lyon}.
-
-\subsubsection{Pulsar Candidate Feature Extraction}
-
-The Python software tool \verb|PulsarFeatureLab| can be used to process pulsar candidate files of the PRESTO Prepfold \verb|PFD| filetype and output the 20 above features for each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype \autocite{lyon}.
-
-To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software are unaffected by the host operating system, a containerised virtual operating system was created using the free software Docker (\verb|https://docker.com|).
+Where candidate features are calculated from the: (1) Integrated Pulsar Profile, (2) the Dispersion Measure -- Signal-to-Noise Ratio Curve (DM-S/N curve), (3) the correlation coefficients between each sub-band and the integrated pulsar profile, and (4) from the correlation coefficients between each sub-integration and the integrated pulsar profile.
+
+A set of 12 pulsar and 13 non-pulsar candidates from the SMART survey were provided by N.
+Swainston to become the machine learning training dataset.
+The free Python software created by \textcite{lyon}, \verb|PulsarFeatureLab|, was used to process the PRESTO Prepfold \verb|PFD| pulsar candidate files, extracting the above 20 machine learning features from each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype.
+To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software were unaffected by the host operating system, a containerised virtual operating system was created using the free software Docker (\verb|https://docker.com|) and the pulsar feature extraction software was thus ran using a bind mounted volume.
+For further details on how this was achieved, see \emph{Appendix \ref{apndx:pulsarfeaturelab}}.
+
+The file outputted by \verb|PulsarFeatureLab| containing the feature extracted candidates was then edited, removing the `?' character and appending a `1' or `0' to the end of each candidate's line depending on whether the candidate was a pulsar or non-pulsar respectively.
+This tells the machine learning classifier that candidates with features similar to those preceding the appended binary classification belong to a pulsar (or a non-pulsar).
+The remaining file constitutes the machine learning training dataset.
+
+\subsection{Developing a Machine Learning Classifier Validation Tool}
+\label{sec:methodvalidate}
+
+In order to automate the evaluation of predictions made by the machine learning pulsar classifiers, a Java program named \verb|PulsarValidator| was developed.
+
+\verb|PulsarValidator| is designed to load the positive and negative output files generated from the machine learning classification of a controlled testing dataset of pulsar candidates, and compare these files to a list of the pulsars included in the testing dataset.
+The software outputs the following statistics: the number of pulsars and non-pulsars, the number of detected pulsars and non-pulsars, and the number of true positives (TP), false positives (FP), true negatives (TN), and false negatives (FN).
+
+This was achieved by first creating individual Java `ArrayList's to contain the filenames of each candidate found to be a True Positive, False Positive, True Negative, or False Negative classification.
+The positive and negative output files generated by the classifier (positive denoting pulsars and negative denoting non-pulsars), and the list of pulsars in the testing dataset are then also converted to Java `ArrayList's.
+The items inside the positive and negative `ArrayList's are then iterated over, checking each item against the list of pulsars.
+If an item in the positive list is found in the list of pulsars, it is added to the True Positive list, otherwise it is added to the False Positive list.
+If an item in the negative list is found in the list of pulsars, it is added to the False Negative list, otherwise it is added to the True Negative list.
+The number of items inside each list is then outputted to the user.
+This process can be seen in \emph{Algorithm \ref{alg:validator}}.
+Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarvalidator}}, and the full Java source code can be found in \emph{Appendix \ref{src:pulsarvalidator}} or on GitHub (\verb|https://github.com/jacob-ian/PulsarValidator.git|).
+
+\begin{algorithm}
+    \caption{Pulsar Validator (pseudocode)}
+    \label{alg:validator}
+    \begin{algorithmic}
+        \State Let $truePositive$ = new List
+        \State Let $falsePositive$ = new List
+        \State Let $trueNegative$ = new List
+        \State Let $falseNegative$ = new List
+
+        \For{each $item$ in $classifierPositive$ list}
+            \State Let Boolean $found$ = false
+            \State Let Integer $i=0$
+            \While{$found$ is false}
+                \If{$i$th item in $pulsarList$ is $item$}
+                    \State add $item$ to $truePositive$ list
+                    \State $found$ = true
+                \ElsIf{$i$ equals number of items in $pulsarList$}
+                    \State add $item$ to $falsePositive$ list
+                    \State $found$ = true
+                \Else
+                    \State $i$=$i+1$
+                \EndIf
+            \EndWhile
+        \EndFor
+
+        \For{each $item$ in $classifierNegative$ list}
+            \State Let Boolean $found$ = false
+            \State Let Integer $i=0$
+            \While{$found$ is false}
+                \If{$i$th item in $pulsarList$ is $item$}
+                    \State add $item$ to $falseNegative$ list
+                    \State $found$ = true
+                \ElsIf{$i$ equals number of items in $pulsarList$}
+                    \State add $item$ to $truePositive$ list
+                    \State $found$ = true
+                \Else
+                    \State $i$=$i+1$
+                \EndIf
+            \EndWhile
+        \EndFor
+        \State Let $TP$ = number of items in $truePositive$
+        \State Let $TN$ = number of items in $trueNegative$
+        \State Let $FP$ = number of items in $falsePositive$
+        \State Let $FN$ = number of items in $falseNegative$
+        \State Let $Pulsars$ = $TP+FN$
+        \State Let $NonPulsars$ = $TN+FP$
+        \State Output $Pulsars$, $NonPulsars$, $TP$, $FP$, $TN$, $FN$
+    \end{algorithmic}
+\end{algorithm}
+
+\subsection{Evaluating the LOTAAS Machine Learning Classification Tool for use with the SMART Survey}
+
+To address the Candidate Selection Problem discussed in \emph{Section 1.3} of this report, a Java Machine Learning pulsar classification tool named \verb|LOTAASClassifier| was created to classify the pulsar candidates produced by the LOFAR Tied-Array All-sky Survey (LOTAAS) \autocite{lyon}.
+Due to the similarities between the LOFAR radio telescope and the Murchison Widefield Array (MWA) radio telescope, it is logical to attempt to apply the \verb|LOTAASClassifier| tool to candidates produced by the MWA.
+
+The \verb|LOTAASClassifier| tool contains four machine learning algorithms with which the user can choose to make pulsar classifications.
+They are: the J48 (C4.5 Decision Tree \autocite{quinlan}), the Multi-Layer Perceptron, the Naive Bayes, and the Support Vector Machines (SVM) algorithms \autocite{lyon}.
+
+To begin evaluating the software, \verb|LOTAASClassifier v1.0| can be downloaded from its GitHub repository \\(\verb|https://github.com/scienceguyrob/LOTAASClassifier|) with the following UNIX terminal commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ git clone https://github.com/scienceguyrob/LOTAASClassifier.git
+\end{lstlisting}
+
+The tool's executable program can then be found by navigating to the following directory in the UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/LOTAASClassifier/dist
+\end{lstlisting}
+
+\subsubsection{Evaluating LOTAASClassifier}
+
+With a successfully created machine learning classification model, it is now possible to test \verb|LOTAASClassifier| against a previously unseen (by the classifier) dataset of Murchison Widefield Array candidates whose class is also known.
+We can first remove the existing candidates from inside the \verb|PFD| files directory and delete the existing \verb|output| files.
+
+The candidates directory can then be populated by new \verb|PFD| files and we can use the `\verb|docker run|' command from \emph{Section 2.2.1} to extract the features from the new candidates.
+
+The \verb|LOTAASClassifier| tool can now make classification predictions on the new candidates by running the UNIX terminal command:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/LOTAASClassifier/dist
+$ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
+\end{lstlisting}
+
+This can be repeated for each machine learning classifier present in the \verb|LOTAASClassifier| software by changing the argument \verb|-a| from 1 through to 4.
+
+We can now run the \verb|PulsarValidator| program created in \emph{Section 2.2.1} to evaluate the accuracy of \verb|LOTAASClassifier|'s algorithms by running the command:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarValidator/target
+$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_[classifier].positive ~/pulsars/data/pfd/output_[classifier].negative
+\end{lstlisting}
+
+Where the \verb|[classifier]| variable can be changed depending on the name of the classifier algorithm being evaluated.
+The outputted validation statistics can then be compared across the algorithms to determine their usefulness with the Murchison Widefield Array.
+
+\subsubsection{Creating the PulsarClassifier Ensemble Classification Tool}
+\label{sec:methodensemble}
+According to \cite{tan}, using Machine Learning algorithms in ensemble to make pulsar classifications increases the accuracy of classifications, classifying pulsars that were often misclassified such as wide-pulse pulsars.
+
+To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ mkdir PulsarClassifier && cd PulsarClassifier
+$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
+\end{lstlisting}
+
+We can now copy the source code from \verb|LOTAASClassifier| to be included in the \verb|PulsarClassifier| software.
+
+\begin{lstlisting}[numbers=none]
+$ cp -R ~/pulsars/LOTAASClassifier/src/ ~/pulsars/PulsarClassifier/src/main/java
+\end{lstlisting}
+
+To use the WEKA suite of Machine Learning tools, we must then edit the \verb|pom.xml| file inside \verb|PulsarClassifier| to include it as a dependency, and resynchronise the project:\\
+
+\begin{lstlisting}[numbers=none, title=pom.xml, language=xml]
+...
+<dependencies>
+...
+    <dependency>
+        <groupId>nz.ac.waikato.cms.weka</groupId>
+        <artifactId>weka-stable</artifactId>
+        <version>3.8.0</version>
+    </dependency>
+...
+</dependencies>
+...
+\end{lstlisting}
+
+We now have the following basic project directory structure:
+
+\begin{lstlisting}[numbers=none]
+PulsarClassifier/
+    src/
+        main/
+            java/
+                com/jacobianmatthews/pulsarclassifier/
+                com/scienceguyrob/lotaasclassifier/
+        test/
+            java/
+                com/jacobianmatthews/pulsarclassifier
+    target/
+            ...
+    pom.xml
+\end{lstlisting}
+
+Where the new source code will be located under \\\verb|/src/main/java/com/jacobianmatthews/pulsarclassifier|.
+To introduce the ensemble classification feature, we must write four main Java classes: \\\verb|PulsarClassifier.java|,  \verb|ClassifierBuilder.java|,  \verb|ClassifierValidator.java|,  and \verb|ClassPredictor.java|.
+
+The \verb|LOTAASClassifier| tool accepts a command-line argument \verb|-a| which accepts an integer that denotes the machine learning algorithm to use in building a classification model and making predictions \autocite{lyon}.
+Therefore, we will add an algorithm into the above listed Java classes that will accept an integer value of \verb|-1| that will activate the ensemble classifier.
+
+The class \verb|ClassifierBuilder.java| handles training and building a classification model. To add ensemble classification to this class we will use the following algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassifierBuilder (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State buildClassifier($i$, $trainingSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Build individual classifier
+            \State buildClassifier($algorithm$, $trainingSet$, $modelPath$)
+
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
+
+The class \verb|ClassifierValidator.java| handles validating and testing the existing classification models.
+To implement the ensemble classifier into this class, we will use the following, similar algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassifierValidator (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State testClassifier($i$, $testSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Test individual classifier
+            \State testClassifier($algorithm$, $testSet$, $modelPath$)
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
+
+The class \verb|ClassPredictor.java| handles making the classification predictions on new data using existing classifier models.
+We can add the ensemble classification feature to this class with the following algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassPredictor (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \State list = new OutputFileList()
+            \For{algorithm $i=1\rightarrow4$}
+                \Comment Loop through all classifiers
+                \State makePredictions($i$, $inputData$, $modelsDirectory$)
+                \State list.add(ClassifierOutputFiles)
+                \Comment Add output filepaths to list
+            \EndFor
+            \State positiveList = new ClassificationsList()
+            \State negativeList = new ClassificationsList()
+            \Comment Create classification lists
+            \For{each OutputFile from list}
+                \If{OutputFile is .positive}
+                    \For{each line in OutputFile}
+                        \State positiveList.add(line)
+                        \Comment Add to +ve classifications
+                    \EndFor
+                \ElsIf{OutputFile is .negative}
+                    \For{each line in OutputFile}
+                        \State negativeList.add(line)
+                        \Comment Add to -ve classifications
+                    \EndFor
+                \EndIf
+            \EndFor
+            \For{each classification in positiveList}
+                \If{classification.occurrences $< 3$}
+                    \State negativeList.add(classification)
+                    \Comment cut-off at $< 3$ classifications
+                \Else
+                    \State positiveOutput(classification)
+                    \Comment Output classified as Pulsar
+                \EndIf
+            \EndFor
+            \For{each classification in negativeList}
+                \State negativeOutput(classification)
+                \Comment Output classified as non-Pulsar
+            \EndFor
+
+        \Else 
+            \State makePredictions($algorithm$)
+            \Comment Use individual classifier
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+The above algorithm preserves the individual classifiers' predictions and also makes an ensemble prediction based on all of the classifiers' predictions.
+According to \cite{tan}, it is common for ensemble machine learning classifiers to use a cut-off of three concurrent positive predictions in separate classifiers to make a positive ensemble classification.
+Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
+See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
+
+The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
+This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
+The complete source code to the \verb|PulsarClassifier| contains the following classes:
+
+\begin{lstlisting}[numbers=none]
+src/
+    main/
+        java/
+            com/jacobianmatthews/pulsarclassifier/
+                utils/
+                    Classification.java
+                    ClassificationList.java
+                    Classifiers.java
+                    Models.java
+                PulsarClassifier.java
+                ClassifierBuilder.java
+                ClassifierValidator.java
+                ClassPredictor.java
+
+            com/scienceguyrob/lotaasclassifier/
+                ...
+
+\end{lstlisting}
+
+Now that the source code for the package is complete, we can add the following lines to the \verb|pom.xml| file at the root of the project:
+
+\pagebreak
+\begin{lstlisting}[numbers=none, language=xml, title=pom.xml, basicstyle=\footnotesize\ttfamily]
+<project>
+    ...
+    <build>
+      <pluginManagement>
+        <plugins>
+          ...
+
+          <!-- Create a JAR containing the resources and dependencies -->
+          <plugin>
+            <groupId>org.apache.maven.plugins</groupId>
+            <artifactId>maven-assembly-plugin</artifactId>
+            <configuration>
+              <archive>
+                <manifest>
+                  <addClasspath>true</addClasspath>
+                  <mainClass>com.jacobianmatthews.pulsarclassifier.PulsarClassifier</mainClass>
+                </manifest>
+              </archive>
+              <descriptorRefs>
+                <descriptorRef>jar-with-dependencies</descriptorRef>
+              </descriptorRefs>
+            </configuration>
+            <executions>
+              <execution>
+                <phase>package</phase>
+                <goals>
+                  <goal>single</goal>
+                </goals>
+              </execution>
+            </executions>
+          </plugin>
+
+          ...
+        </plugins>
+      </pluginManagement>
+    </build>
+    ...
+</project>
+\end{lstlisting}
+
+This will instruct Maven to build a Java \verb|JAR| file containing the package and its WEKA library dependency. To build the package, we can run the following commands in the UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarClassifier
+$ mvn assembly:single
+\end{lstlisting}
+
+The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{sec:pulsarclassifier}}.
+
+\subsubsection{Evaluating PulsarClassifier}
+
+Now that we have successfully built \verb|PulsarClassifier|, we can evaluate its usage with the Murchison Widefield Array's (MWA) candidates. We begin by:
+\begin{enumerate}[label=\roman*.] 
+    \item deleting the previous \verb|output.positive| and \verb|output.negative| files from the \verb|PFD| candidates directory; and
+    \item deleting the previous \verb|model.m| file created by the \verb|LOTAASClassifier| software.
+\end{enumerate}
+
+We can now build the ensemble classification model with the training dataset created earlier, by running the following commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd target
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+Where the argument \verb|-m| now denotes the path to a directory to store the various classifier models.
+Now that we have all of the classification models created, we can use the ensemble classifier to predict the class of new candidates.
+Using the feature extracted candidates compiled from \emph{Section 2.2.2}, we can run the following command:
+
+\begin{lstlisting}[numbers=none]
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+\verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
+We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarValidator/target
+$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_ensemble.positive ~/pulsars/data/pfd/output_ensemble.negative
+\end{lstlisting}
+
+The outputted validation statistics can then be compared to those created for the \verb|LOTAASClassifier| algorithms and an opinion can be formed in regards to the utility of \verb|PulsarClassifier| with the Murchison Widefield Array.
+
+\pagebreak
+% Results Section
+\section{Results and Analyses}
+\subsection{Machine Learning Training Dataset}
+
+The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix \ref{sec:training}}.
+
+\subsection{Classification Results from the LOTAASClassifier Algorithms}
+
+\subsubsection{The J48 Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the J48 (C4.5 Decision Tree) algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 146
+True Positives: 131
+False Positives: 15
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 88
+True Negatives: 72
+False Negatives: 16
+\end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N_p} = \frac{131}{147} =  0.8911 = 89.11\%,$$
+
+where $N_p$ is the number of pulsars in the testing dataset and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{72}{87} = 0.8275 = 82.75\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsubsection{The Multi-Layer Perceptron Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Multi-Layer Perceptron algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 125
+True Positives: 123
+False Positives: 2
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 109
+True Negatives: 85
+False Negatives: 24
+\end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{123}{147} =  0.8367 = 83.67\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{85}{87} = 0.9770 = 97.70\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsubsection{The Naïve Bayes Tester Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 119
+True Positives: 118
+False Positives: 1
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 115
+True Negatives: 86
+False Negatives: 29
+\end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{118}{147} =  0.8027 = 80.27\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{86}{87} = 0.9885 = 98.85\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsubsection{The Support Vector Machine Algorithm}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 97
+True Positives: 97
+False Positives: 0
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 137
+True Negatives: 87
+False Negatives: 50
+\end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{97}{147} =  0.6598 = 65.98\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsection{Classification Results from the PulsarClassifier Ensemble Classifier}
+
+The output created by \verb|PulsarValidator| on analysis of the classification results of the \verb|PulsarClassifier| ensemble classifier is as follows:
+
+\begin{lstlisting}[numbers=none]
+Number of Pulsars: 147
+Pulsars Detected: 112
+True Positives: 112
+False Positives: 0
+
+Number of Non-Pulsars: 87
+Non-Pulsars Detected: 122
+True Negatives: 87
+False Negatives: 35
+\end{lstlisting}
+
+We can therefore calculate the pulsar classification success rate to be:
+
+$$ R_{p} = \frac{TP}{N} = \frac{112}{147} =  0.7619 = 76.19\%,$$
+
+where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
+
+$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
+
+where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
+
+\subsection{Combined Analyses}
+
+A table containing the pulsar and non-pulsar classification success rates of all algorithms and the ensemble classifier can be found below:
+
+\begin{table}[H]
+    \centering
+
+    \caption{Success Rates of Each Pulsar Classifier}
+
+    \begin{framed}
+        \begin{tabular}{l c c c}
+            Classifier & $R_p$ & $R_{np}$ & $Combined$ \\
+            \hline
+            \hline
+            LOTAASClassifier &  &  & \\
+            \hline
+            J48 & 89.11\% & 82.75\% & 85.93\% \\
+            MLP & 83.67\% & 97.70\% & 90.69\% \\
+            NB & 80.27\% & 98.85\% & 89.56\%\\
+            SVM & 65.98\% & 100.00\% & 82.99\% \\
+            \hline
+            PulsarClassifier &  &  & \\
+            \hline
+            Ensemble & 76.19\% & 100.00\% & 88.10\% \\
+        \end{tabular}
+
+        \vspace{5px}
+        $R_p$: Success rate of pulsar classification.\\
+        $R_{np}$: Success rate of non-pulsar classification. \\
+    \end{framed}
+    \label{tab:analyses}
+\end{table}
+
+\pagebreak
+% Results Discussion Section
+\section{Discussion and Conclusions}
+\subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
+
+A pulsar classification pipeline can be defined as the process undertaken to classify a candidate as a pulsar \autocite{swainston}.
+The current pipeline at the Curtin Institute of Radio Astronomy (CIRA) for pulsar classification is as follows:
+\begin{enumerate}[label=\roman*.]
+    \item Generate pulsar candidates through the SMART (Southern-sky MWA Rapid Two-metre) survey;
+    \item Extract machine learning features from the pulsar candidates using \\\verb|PulsarFeatureLab|;
+    \item Use the LOFAR Tied-Array All-Sky machine learning pulsar classifier, \verb|LOTAASClassifier|, to to eliminate a large number of pulsar candidates; and
+    \item Manually inspect the remaining pulsar candidates to confirm pulsar discovery.
+\end{enumerate}
+\autocite{swainston}. While the classification pipeline itself appears to be optimal, I have identified a few issues with the previous attempts at CIRA in using the machine learning classifier.
+
+The first issue revolves around the use of mislabelled and incomplete software.
+In the research completed by \textcite{tan}, the original \\\verb|LOTAASClassifier|, created by \textcite{lyon}, was upgraded to include two major new features: (i) ensemble classification, and (ii) radio frequency interference (RFI) classification.
+The machine learning feature set was also expanded from 8 features in \textcite{lyon} to 20 features in \textcite{tan}, greatly improving the accuracy of classification.
+Upon analysis of the source code of \verb|LOTAASClassifier|, it appears that the two new classification features were not released publicly, despite the software being labelled as \verb|LOTAASClassifier v2.0| in its main Java class, the same name referenced by \textcite{tan}.
+Despite this, the new, expanded set of machine learning features was released with \verb|PulsarFeatureLab Version 1.3.2|.
+This created a mismatch between the feature extraction software and the machine learning classifier, which leads to the next issue in the CIRA pipeline: the training dataset.
+
+In the pipeline provided by \textcite{swainston}, it appears that CIRA has been attempting to use the training dataset generated for the LOFAR Tied-Array All-Sky Survey included with the \verb|LOTAASClassifier| software, for pulsar candidates generated in the SMART survey.
+In itself, this may not present issues, however due to the unknown mismatch in the machine learning software, an issue of feature dimensions occurs.
+The included training dataset creates a classification model with the original 8 machine learning features, therefore any predictions on new candidates would require the same 8 machine learning features to have been extracted prior to classification.
+Due to the mislabelled software, CIRA has been extracting the set of 20 features from pulsar candidates and attempting to make classifications against a set of 8 features, preventing classifications from occurring in \verb|LOTAASClassifier| due to a mismatch in dimensions.
+This issue can be fixed by creating a training dataset with the same set of extracted features as will be present in the candidates for classification.
+
+The final issue arising in the CIRA pipeline also spouts from the mislabelling of the \verb|LOTAASClassifier| software.
+The CIRA pipeline expects that the ensemble classifier created in the upgraded software from \textcite{tan} will be used.
+Without the latest version of \verb|LOTAASClassifier| having been released, the CIRA pipeline defaults to using the J48 machine learning classification algorithm.
+As seen in Table \ref{tab:analyses} from \emph{Section 3.4}, the J48 algorithm does not appear to be optimal in combined pulsar and non-pulsar classification.
+To fix this issue, an ensemble machine learning classifier was created in \emph{Section 2.2.4} to replace the \verb|LOTAASClassifier| software.
+
+\subsection{Evaluating the Training Dataset and Machine Learning Classifiers}
+
+An evaluation of the machine learning classifiers: \verb|LOTAASClassifier| and its algorithms, and \verb|PulsarClassfier|, will in its nature be subject to the quality of the training dataset used.
+By inspecting the data produced in \emph{Section 3.2}, we can see the success rates of pulsar and non-pulsar classification, which are defined as the ratio of the number of true positive (true negative) classifications with the number of pulsars (non-pulsars).
+The success rates of each classifier are then compiled into Table \ref{tab:analyses}.
+Another metric, the combined success rate, is also introduced as the mean of the two success rates.
+The combined success rate can be used to rank the total accuracy of the classifiers, however this metric does not contain ample information.
+The classifiers can thus be ranked in order of highest total accuracy:
+
+\begin{enumerate}
+    \item Multi-Layered Perceptron (90.69\%)
+    \item Naïve Bayes Test (89.56\%)
+    \item Ensemble Classifier (88.10\%)
+    \item J48 (C4.5 Decision Tree) (85.93\%)
+    \item Support Vector Machine (82.99\%)
+\end{enumerate}
+
+Despite being ranked third in combined success rates, the \verb|PulsarClassifier|'s Ensemble Classifier was only one of two classifiers that correctly classified all examples of noise and radio frequency interference as \emph{non-pulsar}, the other successful classifier being the Support Vector Machine.
+As a result of this, there were no false positive classifications completed by the Ensemble classifier, i.e.
+everything classified as a pulsar actually was a pulsar.
+The Ensemble Classifier was let down by misclassifying 35 pulsars, having the second-lowest success rate of pulsar classification - the lowest being the Support Vector Machine which misclassified 50 pulsars, and the highest being the J48 Classifier having misclassified only 16 pulsars.
+
+For the use case of classifying pulsar candidates generated from the Murchison Widefield Array, the most important metric to be considered when evaluating a machine learning classifier is the pulsar classification success rate.
+It is more important to not miss the classification of a pulsar and less important if a non-pulsar is classified as a pulsar.
+For this reason, the objective is to maximise the rate of true positive classifications and minimise the rate of false negative classifications.
+
+The training dataset created in this project contained 11 examples of pulsars and 12 examples of noise and radio frequency interference (RFI).
+While the training dataset appeared to have a satisfactory variety of noise and RFI, contributing to the ensemble classifier's perfect rate of non-pulsar classification, the set of pulsars appeared to be unsatisfactory.
+In order to improve the success rate of pulsar classification (positive success rate) in the ensemble classifier, we must use a modified training dataset that will improve the positive success rate in the worst performing individual classifiers: the Support Vector Machine (65.98\%), and the Naïve Bayes Test (80.27\%), whilst maintaining the higher positive success rates of the other classifiers.
+By doing so, more pulsars will survive the ensemble classifier's individual classification criteria of 3 or more, and thus the positive success rate will improve.
+This modification to the training dataset could involve changing the included set of pulsars to include a subset of pulsars of ordinary appearing features, and the remaining subset of pulsars should exhibit unusual or difficult to discern features.
+
+In conclusion, I believe that the machine learning classifiers in the \\\verb|LOTAASClassifier| software, particularly used in ensemble such as with the \verb|PulsarClassifier| software created for this project, are of great utility for current and future Murchison Widefield Array pulsar surveys.
+As discussed in \textcite{lyon}, the number of pulsar candidates generated in pulsar surveys stands to grow exponentially beyond the economical capacity of data storage and viability of manual examination.
+This problem requires a solution to filter out the non-pulsars from the group of candidates to maximise the discovery of pulsars, and I believe that the \verb|PulsarClassifier| software is another step forward in solving the problem.
+While the training dataset does require further development to maximise the success of the Ensemble Classifier, the Machine Learning techniques themselves proved to be extremely valuable in pulsar classification.
+
+\pagebreak
+% RECOMMENDATIONS SECTION
+\section{Recommendations}
+
+For further development of the Machine Learning classifiers and strategies used in this project, I would recommend undertaking the following tasks:
+
+\begin{enumerate}
+    \item Investigate and fix the Python \verb|Traceback Error| produced by the software \verb|PulsarFeatureLab v1.3.2|:
+
+    During the usage of this feature extraction software, some \verb|PFD| candidate files would cause a \verb|Traceback| error to be produced, causing the feature extraction to fail for that particular candidate.
+The result of these failures was that there was a smaller dataset to train the machine learning classifiers on, and a smaller dataset to make machine learning classification predictions on.
+
+    \item Build the Radio Frequency Interference (RFI) classification feature discussed by \textcite{tan} into \verb|PulsarClassifier|:
+
+    According to \textcite{tan}, by also including the classification category of RFI, the accuracy of the machine learning ensemble classifier was increased.
+The result of this feature would be three classifier output files: \verb|output.pulsars|, \verb|output.rfi|, and \verb|output.other|.
+
+    \item Use a more diverse Training Dataset:
+
+    Due to constraints on the available \verb|PFD| candidate data during this project, I was unable to use a large set of pulsar and non-pulsar candidates in the training dataset.
+By using a training dataset that is more diverse, the \verb|PulsarClassifier| will be more accurate in its predictions.
+\end{enumerate}
+
+\pagebreak
+% REFERENCES SECTION
+\section{References}
+\printbibliography[heading=none]
+
+\pagebreak
+% APPENDICES SECTION
+\begin{appendices}
+
+    \section{Methods}
+    \begin{subappendices}
+        \subsection{Feature Extraction with PulsarFeatureLab}
+        \label{apndx:pulsarfeaturelab}
 
@@
 
-Candidate \verb|PFD| files of known pulsars and non-pulsars detected by the Murchison Widefield Array (MWA) provided by N.
-Swainston can now populate the above created directory, and the following command can be ran to extract the features from the candidates:
+        For future development of this project, the Docker image \\\verb|jacobianm/pulsarfeaturelab:1.3.2| is available on Docker Hub\\(\verb|https://hub.docker.com|) and will be automatically downloaded when running the \verb|docker run| command below.
+Candidate \verb|PFD| files of known pulsars and non-pulsars detected by the Murchison Widefield Array (MWA) can now populate the above created directory, and the following command can be ran to extract the features from the candidates:
 
@@
 
-This function instructs Docker to connect the directory containing the \verb|PFD| files to the \verb|PulsarFeatureLab| container's input/output directory and then run the \verb|PulsarFeatureLab| software with arguments stating where the input files are, what filetype they are (\verb|PFD|), which set of features to extract, and where to place the output file.
-
-\subsubsection{Creating the Training Dataset}
-
-The \verb|output.arff| file created by \verb|PulsarFeatureLab|, contains a set of comma-separated features for each candidate, with an appended `?' character, per file line.
-Since the class of each candidate is already known, the `?' character on each line can be replaced by a `1' if the candidate is a pulsar, or a `0' if the candidate is a non-pulsar.
-This signals to the Machine Learning algorithm what a pulsar and a non-pulsar candidate's feature set may appear like.
-
-The edited file can now be renamed and moved with the following command:
-
-\begin{lstlisting}[numbers=none]
-$ mv ~/pulsars/data/pfd/output.arff ~/pulsars/data/trainingSet.arff
-\end{lstlisting}
-
-The Machine Learning Training Dataset has now been created using Murchison Widefield Array data.
-
-\subsection{Evaluating the LOTAASClassifier Machine Learning Classification Tool for use with the Murchison Widefield Array}
-
-To address the Candidate Selection Problem discussed in \emph{Section 1.3} of this report, a Java Machine Learning pulsar classification tool named \verb|LOTAASClassifier| was created to classify the pulsar candidates produced by the LOFAR Tied-Array All-sky Survey (LOTAAS) \autocite{lyon}.
-Due to the similarities between the LOFAR radio telescope and the Murchison Widefield Array (MWA) radio telescope, it is logical to attempt to apply the \verb|LOTAASClassifier| tool to candidates produced by the MWA.
-
-The \verb|LOTAASClassifier| tool contains four machine learning algorithms with which the user can choose to make pulsar classifications.
-They are: the J48 (C4.5 Decision Tree \autocite{quinlan}), the Multi-Layer Perceptron, the Naive Bayes, and the Support Vector Machines (SVM) algorithms \autocite{lyon}.
-
-To begin evaluating the software, \verb|LOTAASClassifier v1.0| can be downloaded from its GitHub repository \\(\verb|https://github.com/scienceguyrob/LOTAASClassifier|) with the following UNIX terminal commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars
-$ git clone https://github.com/scienceguyrob/LOTAASClassifier.git
-\end{lstlisting}
-
-The tool's executable program can then be found by navigating to the following directory in the UNIX terminal:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/LOTAASClassifier/dist
-\end{lstlisting}
-
-\subsubsection{Creating a Pulsar Classifier Output Validation Tool}
-\label{sec:methodvalidate}
-In order to accurately evaluate and test the predictions made by the \verb|LOTAASClassifier| tool, we must create a program that will automate the process of checking the outputs of the classifier against the known list of pulsars.
-
+        This function instructs Docker to connect the directory containing the \verb|PFD| files to the \verb|PulsarFeatureLab| container's input/output directory and then run the \verb|PulsarFeatureLab| software with arguments stating where the input files are, what filetype they are (\verb|PFD|), which set of features to extract, and where to place the output file (\verb|output.arff|).
+
+        \subsection{Developing PulsarValidator}
+        \label{apndx:pulsarvalidator}
         We begin by creating a new Java project using the free software Maven (\verb|https://maven.apache.org|) by running the following commands in a UNIX terminal:
@@
 
-This software will consume a user inputted \verb|String| containing the path to a file with the list of pulsars included in the dataset classified by the machine learning classifier, a user inputted \verb|String| containing the path to the \verb|.positive| file created by the classifier, and a user inputted \verb|String| containing the path to the \verb|.negative| file created by the classifier\footnote{The '.positive' file contains the candidates classified as pulsars, and the '.negative' file contains the candidates classified as non-pulsars.}.
+        This software will process a user inputted \verb|String| containing the path to a file with the list of pulsars included in the dataset classified by the machine learning classifier, a user inputted \verb|String| containing the path to the \verb|.positive| file created by the classifier, and a user inputted \verb|String| containing the path to the \verb|.negative| file created by the classifier\footnote{The '.positive' file contains the candidates classified as pulsars, and the '.negative' file contains the candidates classified as non-pulsars.}.
 These will be inputted as command-line arguments when the user runs the Java executable file.
@@
 
-\subsubsection{Creating a Classification Model}
+        \subsection{Creating a Classification Model with LOTAASClassifier}
 
@@
 The J48 classification model was constructed successfully if the candidates inside the `\verb|positive|' file are the known pulsars.
-
-\subsubsection{Evaluating LOTAASClassifier}
-
-With a successfully created machine learning classification model, it is now possible to test \verb|LOTAASClassifier| against a previously unseen (by the classifier) dataset of Murchison Widefield Array candidates whose class is also known.
-We can first remove the existing candidates from inside the \verb|PFD| files directory and delete the existing \verb|output| files.
-
-The candidates directory can then be populated by new \verb|PFD| files and we can use the `\verb|docker run|' command from \emph{Section 2.2.1} to extract the features from the new candidates.
-
-The \verb|LOTAASClassifier| tool can now make classification predictions on the new candidates by running the UNIX terminal command:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/LOTAASClassifier/dist
-$ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
-\end{lstlisting}
-
-This can be repeated for each machine learning classifier present in the \verb|LOTAASClassifier| software by changing the argument \verb|-a| from 1 through to 4.
-
-We can now run the \verb|PulsarValidator| program created in \emph{Section 2.2.1} to evaluate the accuracy of \verb|LOTAASClassifier|'s algorithms by running the command:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarValidator/target
-$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_[classifier].positive ~/pulsars/data/pfd/output_[classifier].negative
-\end{lstlisting}
-
-Where the \verb|[classifier]| variable can be changed depending on the name of the classifier algorithm being evaluated.
-The outputted validation statistics can then be compared across the algorithms to determine their usefulness with the Murchison Widefield Array.
-
-\subsubsection{Creating the PulsarClassifier Ensemble Classification Tool}
-\label{sec:methodensemble}
-According to \cite{tan}, using Machine Learning algorithms in ensemble to make pulsar classifications increases the accuracy of classifications, classifying pulsars that were often misclassified such as wide-pulse pulsars.
-
-To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars
-$ mkdir PulsarClassifier && cd PulsarClassifier
-$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
-\end{lstlisting}
-
-We can now copy the source code from \verb|LOTAASClassifier| to be included in the \verb|PulsarClassifier| software.
-
-\begin{lstlisting}[numbers=none]
-$ cp -R ~/pulsars/LOTAASClassifier/src/ ~/pulsars/PulsarClassifier/src/main/java
-\end{lstlisting}
-
-To use the WEKA suite of Machine Learning tools, we must then edit the \verb|pom.xml| file inside \verb|PulsarClassifier| to include it as a dependency, and resynchronise the project:\\
-
-\begin{lstlisting}[numbers=none, title=pom.xml, language=xml]
-...
-<dependencies>
-...
-    <dependency>
-        <groupId>nz.ac.waikato.cms.weka</groupId>
-        <artifactId>weka-stable</artifactId>
-        <version>3.8.0</version>
-    </dependency>
-...
-</dependencies>
-...
-\end{lstlisting}
-
-We now have the following basic project directory structure:
-
-\begin{lstlisting}[numbers=none]
-PulsarClassifier/
-    src/
-        main/
-            java/
-                com/jacobianmatthews/pulsarclassifier/
-                com/scienceguyrob/lotaasclassifier/
-        test/
-            java/
-                com/jacobianmatthews/pulsarclassifier
-    target/
-            ...
-    pom.xml
-\end{lstlisting}
-
-Where the new source code will be located under \\\verb|/src/main/java/com/jacobianmatthews/pulsarclassifier|.
-To introduce the ensemble classification feature, we must write four main Java classes: \\\verb|PulsarClassifier.java|,  \verb|ClassifierBuilder.java|,  \verb|ClassifierValidator.java|,  and \verb|ClassPredictor.java|.
-
-The \verb|LOTAASClassifier| tool accepts a command-line argument \verb|-a| which accepts an integer that denotes the machine learning algorithm to use in building a classification model and making predictions \autocite{lyon}.
-Therefore, we will add an algorithm into the above listed Java classes that will accept an integer value of \verb|-1| that will activate the ensemble classifier.
-
-The class \verb|ClassifierBuilder.java| handles training and building a classification model. To add ensemble classification to this class we will use the following algorithm:
-
-\begin{algorithm}[H]
-    \caption{ClassifierBuilder (pseudocode)}
-    \begin{algorithmic}[1]
-        \If{$algorithm = -1$}
-            \For{each algorithm $i=1\rightarrow 4$}
-                \Comment Loop through all classifiers
-                \State buildClassifier($i$, $trainingSet$, $modelsDirectory$)
-            \EndFor
-        \Else 
-            \Comment Build individual classifier
-            \State buildClassifier($algorithm$, $trainingSet$, $modelPath$)
-
-        \EndIf
-
-    \end{algorithmic}
-\end{algorithm}
-
-See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
-
-The class \verb|ClassifierValidator.java| handles validating and testing the existing classification models.
-To implement the ensemble classifier into this class, we will use the following, similar algorithm:
-
-\begin{algorithm}[H]
-    \caption{ClassifierValidator (pseudocode)}
-    \begin{algorithmic}[1]
-        \If{$algorithm = -1$}
-            \For{each algorithm $i=1\rightarrow 4$}
-                \Comment Loop through all classifiers
-                \State testClassifier($i$, $testSet$, $modelsDirectory$)
-            \EndFor
-        \Else 
-            \Comment Test individual classifier
-            \State testClassifier($algorithm$, $testSet$, $modelPath$)
-        \EndIf
-
-    \end{algorithmic}
-\end{algorithm}
-
-See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
-
-The class \verb|ClassPredictor.java| handles making the classification predictions on new data using existing classifier models.
-We can add the ensemble classification feature to this class with the following algorithm:
-
-\begin{algorithm}[H]
-    \caption{ClassPredictor (pseudocode)}
-    \begin{algorithmic}[1]
-        \If{$algorithm = -1$}
-            \State list = new OutputFileList()
-            \For{algorithm $i=1\rightarrow4$}
-                \Comment Loop through all classifiers
-                \State makePredictions($i$, $inputData$, $modelsDirectory$)
-                \State list.add(ClassifierOutputFiles)
-                \Comment Add output filepaths to list
-            \EndFor
-            \State positiveList = new ClassificationsList()
-            \State negativeList = new ClassificationsList()
-            \Comment Create classification lists
-            \For{each OutputFile from list}
-                \If{OutputFile is .positive}
-                    \For{each line in OutputFile}
-                        \State positiveList.add(line)
-                        \Comment Add to +ve classifications
-                    \EndFor
-                \ElsIf{OutputFile is .negative}
-                    \For{each line in OutputFile}
-                        \State negativeList.add(line)
-                        \Comment Add to -ve classifications
-                    \EndFor
-                \EndIf
-            \EndFor
-            \For{each classification in positiveList}
-                \If{classification.occurrences $< 3$}
-                    \State negativeList.add(classification)
-                    \Comment cut-off at $< 3$ classifications
-                \Else
-                    \State positiveOutput(classification)
-                    \Comment Output classified as Pulsar
-                \EndIf
-            \EndFor
-            \For{each classification in negativeList}
-                \State negativeOutput(classification)
-                \Comment Output classified as non-Pulsar
-            \EndFor
-
-        \Else 
-            \State makePredictions($algorithm$)
-            \Comment Use individual classifier
-        \EndIf
-
-    \end{algorithmic}
-\end{algorithm}
-
-The above algorithm preserves the individual classifiers' predictions and also makes an ensemble prediction based on all of the classifiers' predictions.
-According to \cite{tan}, it is common for ensemble machine learning classifiers to use a cut-off of three concurrent positive predictions in separate classifiers to make a positive ensemble classification.
-Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
-See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
-
-The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
-This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
-The complete source code to the \verb|PulsarClassifier| contains the following classes:
-
-\begin{lstlisting}[numbers=none]
-src/
-    main/
-        java/
-            com/jacobianmatthews/pulsarclassifier/
-                utils/
-                    Classification.java
-                    ClassificationList.java
-                    Classifiers.java
-                    Models.java
-                PulsarClassifier.java
-                ClassifierBuilder.java
-                ClassifierValidator.java
-                ClassPredictor.java
-
-            com/scienceguyrob/lotaasclassifier/
-                ...
-
-\end{lstlisting}
-
-Now that the source code for the package is complete, we can add the following lines to the \verb|pom.xml| file at the root of the project:
-
-\pagebreak
-\begin{lstlisting}[numbers=none, language=xml, title=pom.xml, basicstyle=\footnotesize\ttfamily]
-<project>
-    ...
-    <build>
-      <pluginManagement>
-        <plugins>
-          ...
-
-          <!-- Create a JAR containing the resources and dependencies -->
-          <plugin>
-            <groupId>org.apache.maven.plugins</groupId>
-            <artifactId>maven-assembly-plugin</artifactId>
-            <configuration>
-              <archive>
-                <manifest>
-                  <addClasspath>true</addClasspath>
-                  <mainClass>com.jacobianmatthews.pulsarclassifier.PulsarClassifier</mainClass>
-                </manifest>
-              </archive>
-              <descriptorRefs>
-                <descriptorRef>jar-with-dependencies</descriptorRef>
-              </descriptorRefs>
-            </configuration>
-            <executions>
-              <execution>
-                <phase>package</phase>
-                <goals>
-                  <goal>single</goal>
-                </goals>
-              </execution>
-            </executions>
-          </plugin>
-
-          ...
-        </plugins>
-      </pluginManagement>
-    </build>
-    ...
-</project>
-\end{lstlisting}
-
-This will instruct Maven to build a Java \verb|JAR| file containing the package and its WEKA library dependency. To build the package, we can run the following commands in the UNIX terminal:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarClassifier
-$ mvn assembly:single
-\end{lstlisting}
-
-The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{sec:pulsarclassifier}}.
-
-\subsubsection{Evaluating PulsarClassifier}
-
-Now that we have successfully built \verb|PulsarClassifier|, we can evaluate its usage with the Murchison Widefield Array's (MWA) candidates. We begin by:
-\begin{enumerate}[label=\roman*.] 
-    \item deleting the previous \verb|output.positive| and \verb|output.negative| files from the \verb|PFD| candidates directory; and
-    \item deleting the previous \verb|model.m| file created by the \verb|LOTAASClassifier| software.
-\end{enumerate}
-
-We can now build the ensemble classification model with the training dataset created earlier, by running the following commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd target
-$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/models -a -1
-\end{lstlisting}
-
-Where the argument \verb|-m| now denotes the path to a directory to store the various classifier models.
-Now that we have all of the classification models created, we can use the ensemble classifier to predict the class of new candidates.
-Using the feature extracted candidates compiled from \emph{Section 2.2.2}, we can run the following command:
-
-\begin{lstlisting}[numbers=none]
-$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/models -a -1
-\end{lstlisting}
-
-\verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
-We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarValidator/target
-$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_ensemble.positive ~/pulsars/data/pfd/output_ensemble.negative
-\end{lstlisting}
-
-The outputted validation statistics can then be compared to those created for the \verb|LOTAASClassifier| algorithms and an opinion can be formed in regards to the utility of \verb|PulsarClassifier| with the Murchison Widefield Array.
-
-\pagebreak
-% Results Section
-\section{Results and Analyses}
-\subsection{Machine Learning Training Dataset}
-
-The machine learning training dataset created with candidates detected by the Murchison Widefield Array can be found under \emph{Appendix \ref{sec:training}}.
-
-\subsection{Classification Results from the LOTAASClassifier Algorithms}
-
-\subsubsection{The J48 Algorithm}
-
-The output created by \verb|PulsarValidator| on analysis of the classification results of the J48 (C4.5 Decision Tree) algorithm is as follows:
-
-\begin{lstlisting}[numbers=none]
-Number of Pulsars: 147
-Pulsars Detected: 146
-True Positives: 131
-False Positives: 15
-
-Number of Non-Pulsars: 87
-Non-Pulsars Detected: 88
-True Negatives: 72
-False Negatives: 16
-\end{lstlisting}
-
-We can therefore calculate the pulsar classification success rate to be:
-
-$$ R_{p} = \frac{TP}{N_p} = \frac{131}{147} =  0.8911 = 89.11\%,$$
-
-where $N_p$ is the number of pulsars in the testing dataset and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
-
-$$R_{np} = \frac{TN}{N_{np}} = \frac{72}{87} = 0.8275 = 82.75\%,$$
-
-where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
-
-\subsubsection{The Multi-Layer Perceptron Algorithm}
-
-The output created by \verb|PulsarValidator| on analysis of the classification results of the Multi-Layer Perceptron algorithm is as follows:
-
-\begin{lstlisting}[numbers=none]
-Number of Pulsars: 147
-Pulsars Detected: 125
-True Positives: 123
-False Positives: 2
-
-Number of Non-Pulsars: 87
-Non-Pulsars Detected: 109
-True Negatives: 85
-False Negatives: 24
-\end{lstlisting}
-
-We can therefore calculate the pulsar classification success rate to be:
-
-$$ R_{p} = \frac{TP}{N} = \frac{123}{147} =  0.8367 = 83.67\%,$$
-
-where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
-
-$$R_{np} = \frac{TN}{N_{np}} = \frac{85}{87} = 0.9770 = 97.70\%,$$
-
-where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
-
-\subsubsection{The Naïve Bayes Tester Algorithm}
-
-The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
-
-\begin{lstlisting}[numbers=none]
-Number of Pulsars: 147
-Pulsars Detected: 119
-True Positives: 118
-False Positives: 1
-
-Number of Non-Pulsars: 87
-Non-Pulsars Detected: 115
-True Negatives: 86
-False Negatives: 29
-\end{lstlisting}
-
-We can therefore calculate the pulsar classification success rate to be:
-
-$$ R_{p} = \frac{TP}{N} = \frac{118}{147} =  0.8027 = 80.27\%,$$
-
-where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
-
-$$R_{np} = \frac{TN}{N_{np}} = \frac{86}{87} = 0.9885 = 98.85\%,$$
-
-where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
-
-\subsubsection{The Support Vector Machine Algorithm}
-
-The output created by \verb|PulsarValidator| on analysis of the classification results of the Naïve Bayes algorithm is as follows:
-
-\begin{lstlisting}[numbers=none]
-Number of Pulsars: 147
-Pulsars Detected: 97
-True Positives: 97
-False Positives: 0
-
-Number of Non-Pulsars: 87
-Non-Pulsars Detected: 137
-True Negatives: 87
-False Negatives: 50
-\end{lstlisting}
-
-We can therefore calculate the pulsar classification success rate to be:
-
-$$ R_{p} = \frac{TP}{N} = \frac{97}{147} =  0.6598 = 65.98\%,$$
-
-where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
-
-$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
-
-where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
-
-\subsection{Classification Results from the PulsarClassifier Ensemble Classifier}
-
-The output created by \verb|PulsarValidator| on analysis of the classification results of the \verb|PulsarClassifier| ensemble classifier is as follows:
-
-\begin{lstlisting}[numbers=none]
-Number of Pulsars: 147
-Pulsars Detected: 112
-True Positives: 112
-False Positives: 0
-
-Number of Non-Pulsars: 87
-Non-Pulsars Detected: 122
-True Negatives: 87
-False Negatives: 35
-\end{lstlisting}
-
-We can therefore calculate the pulsar classification success rate to be:
-
-$$ R_{p} = \frac{TP}{N} = \frac{112}{147} =  0.7619 = 76.19\%,$$
-
-where $N$ is the number of pulsars in the testing dataset, and $TP$ is the number of true positive classifications. The non-pulsar classification success rate can be found as:
-
-$$R_{np} = \frac{TN}{N_{np}} = \frac{87}{87} = 1.00 = 100.00\%,$$
-
-where $N_{np}$ is the number of non-pulsars in the testing dataset and $TN$ is the number of true negative classifications.
-
-\subsection{Combined Analyses}
-
-A table containing the pulsar and non-pulsar classification success rates of all algorithms and the ensemble classifier can be found below:
-
-\begin{table}[H]
-    \centering
-
-    \caption{Success Rates of Each Pulsar Classifier}
-
-    \begin{framed}
-        \begin{tabular}{l c c c}
-            Classifier & $R_p$ & $R_{np}$ & $Combined$ \\
-            \hline
-            \hline
-            LOTAASClassifier &  &  & \\
-            \hline
-            J48 & 89.11\% & 82.75\% & 85.93\% \\
-            MLP & 83.67\% & 97.70\% & 90.69\% \\
-            NB & 80.27\% & 98.85\% & 89.56\%\\
-            SVM & 65.98\% & 100.00\% & 82.99\% \\
-            \hline
-            PulsarClassifier &  &  & \\
-            \hline
-            Ensemble & 76.19\% & 100.00\% & 88.10\% \\
-        \end{tabular}
-
-        \vspace{5px}
-        $R_p$: Success rate of pulsar classification.\\
-        $R_{np}$: Success rate of non-pulsar classification. \\
-    \end{framed}
-    \label{tab:analyses}
-\end{table}
-
-\pagebreak
-% Results Discussion Section
-\section{Discussion and Conclusions}
-\subsection{Evaluating Curtin Institute of Radio Astronomy's Pulsar Classification Pipeline}
-
-A pulsar classification pipeline can be defined as the process undertaken to classify a candidate as a pulsar \autocite{swainston}.
-The current pipeline at the Curtin Institute of Radio Astronomy (CIRA) for pulsar classification is as follows:
-\begin{enumerate}[label=\roman*.]
-    \item Generate pulsar candidates through the SMART (Southern-sky MWA Rapid Two-metre) survey;
-    \item Extract machine learning features from the pulsar candidates using \\\verb|PulsarFeatureLab|;
-    \item Use the LOFAR Tied-Array All-Sky machine learning pulsar classifier, \verb|LOTAASClassifier|, to to eliminate a large number of pulsar candidates; and
-    \item Manually inspect the remaining pulsar candidates to confirm pulsar discovery.
-\end{enumerate}
-\autocite{swainston}. While the classification pipeline itself appears to be optimal, I have identified a few issues with the previous attempts at CIRA in using the machine learning classifier.
-
-The first issue revolves around the use of mislabelled and incomplete software.
-In the research completed by \textcite{tan}, the original \\\verb|LOTAASClassifier|, created by \textcite{lyon}, was upgraded to include two major new features: (i) ensemble classification, and (ii) radio frequency interference (RFI) classification.
-The machine learning feature set was also expanded from 8 features in \textcite{lyon} to 20 features in \textcite{tan}, greatly improving the accuracy of classification.
-Upon analysis of the source code of \verb|LOTAASClassifier|, it appears that the two new classification features were not released publicly, despite the software being labelled as \verb|LOTAASClassifier v2.0| in its main Java class, the same name referenced by \textcite{tan}.
-Despite this, the new, expanded set of machine learning features was released with \verb|PulsarFeatureLab Version 1.3.2|.
-This created a mismatch between the feature extraction software and the machine learning classifier, which leads to the next issue in the CIRA pipeline: the training dataset.
-
-In the pipeline provided by \textcite{swainston}, it appears that CIRA has been attempting to use the training dataset generated for the LOFAR Tied-Array All-Sky Survey included with the \verb|LOTAASClassifier| software, for pulsar candidates generated in the SMART survey.
-In itself, this may not present issues, however due to the unknown mismatch in the machine learning software, an issue of feature dimensions occurs.
-The included training dataset creates a classification model with the original 8 machine learning features, therefore any predictions on new candidates would require the same 8 machine learning features to have been extracted prior to classification.
-Due to the mislabelled software, CIRA has been extracting the set of 20 features from pulsar candidates and attempting to make classifications against a set of 8 features, preventing classifications from occurring in \verb|LOTAASClassifier| due to a mismatch in dimensions.
-This issue can be fixed by creating a training dataset with the same set of extracted features as will be present in the candidates for classification.
-
-The final issue arising in the CIRA pipeline also spouts from the mislabelling of the \verb|LOTAASClassifier| software.
-The CIRA pipeline expects that the ensemble classifier created in the upgraded software from \textcite{tan} will be used.
-Without the latest version of \verb|LOTAASClassifier| having been released, the CIRA pipeline defaults to using the J48 machine learning classification algorithm.
-As seen in Table \ref{tab:analyses} from \emph{Section 3.4}, the J48 algorithm does not appear to be optimal in combined pulsar and non-pulsar classification.
-To fix this issue, an ensemble machine learning classifier was created in \emph{Section 2.2.4} to replace the \verb|LOTAASClassifier| software.
-
-\subsection{Evaluating the Training Dataset and Machine Learning Classifiers}
-
-An evaluation of the machine learning classifiers: \verb|LOTAASClassifier| and its algorithms, and \verb|PulsarClassfier|, will in its nature be subject to the quality of the training dataset used.
-By inspecting the data produced in \emph{Section 3.2}, we can see the success rates of pulsar and non-pulsar classification, which are defined as the ratio of the number of true positive (true negative) classifications with the number of pulsars (non-pulsars).
-The success rates of each classifier are then compiled into Table \ref{tab:analyses}.
-Another metric, the combined success rate, is also introduced as the mean of the two success rates.
-The combined success rate can be used to rank the total accuracy of the classifiers, however this metric does not contain ample information.
-The classifiers can thus be ranked in order of highest total accuracy:
-
-\begin{enumerate}
-    \item Multi-Layered Perceptron (90.69\%)
-    \item Naïve Bayes Test (89.56\%)
-    \item Ensemble Classifier (88.10\%)
-    \item J48 (C4.5 Decision Tree) (85.93\%)
-    \item Support Vector Machine (82.99\%)
-\end{enumerate}
-
-Despite being ranked third in combined success rates, the \verb|PulsarClassifier|'s Ensemble Classifier was only one of two classifiers that correctly classified all examples of noise and radio frequency interference as \emph{non-pulsar}, the other successful classifier being the Support Vector Machine.
-As a result of this, there were no false positive classifications completed by the Ensemble classifier, i.e.
-everything classified as a pulsar actually was a pulsar.
-The Ensemble Classifier was let down by misclassifying 35 pulsars, having the second-lowest success rate of pulsar classification - the lowest being the Support Vector Machine which misclassified 50 pulsars, and the highest being the J48 Classifier having misclassified only 16 pulsars.
-
-For the use case of classifying pulsar candidates generated from the Murchison Widefield Array, the most important metric to be considered when evaluating a machine learning classifier is the pulsar classification success rate.
-It is more important to not miss the classification of a pulsar and less important if a non-pulsar is classified as a pulsar.
-For this reason, the objective is to maximise the rate of true positive classifications and minimise the rate of false negative classifications.
-
-The training dataset created in this project contained 11 examples of pulsars and 12 examples of noise and radio frequency interference (RFI).
-While the training dataset appeared to have a satisfactory variety of noise and RFI, contributing to the ensemble classifier's perfect rate of non-pulsar classification, the set of pulsars appeared to be unsatisfactory.
-In order to improve the success rate of pulsar classification (positive success rate) in the ensemble classifier, we must use a modified training dataset that will improve the positive success rate in the worst performing individual classifiers: the Support Vector Machine (65.98\%), and the Naïve Bayes Test (80.27\%), whilst maintaining the higher positive success rates of the other classifiers.
-By doing so, more pulsars will survive the ensemble classifier's individual classification criteria of 3 or more, and thus the positive success rate will improve.
-This modification to the training dataset could involve changing the included set of pulsars to include a subset of pulsars of ordinary appearing features, and the remaining subset of pulsars should exhibit unusual or difficult to discern features.
-
-In conclusion, I believe that the machine learning classifiers in the \\\verb|LOTAASClassifier| software, particularly used in ensemble such as with the \verb|PulsarClassifier| software created for this project, are of great utility for current and future Murchison Widefield Array pulsar surveys.
-As discussed in \textcite{lyon}, the number of pulsar candidates generated in pulsar surveys stands to grow exponentially beyond the economical capacity of data storage and viability of manual examination.
-This problem requires a solution to filter out the non-pulsars from the group of candidates to maximise the discovery of pulsars, and I believe that the \verb|PulsarClassifier| software is another step forward in solving the problem.
-While the training dataset does require further development to maximise the success of the Ensemble Classifier, the Machine Learning techniques themselves proved to be extremely valuable in pulsar classification.
-
-\pagebreak
-% RECOMMENDATIONS SECTION
-\section{Recommendations}
-
-For further development of the Machine Learning classifiers and strategies used in this project, I would recommend undertaking the following tasks:
-
-\begin{enumerate}
-    \item Investigate and fix the Python \verb|Traceback Error| produced by the software \verb|PulsarFeatureLab v1.3.2|:
-
-    During the usage of this feature extraction software, some \verb|PFD| candidate files would cause a \verb|Traceback| error to be produced, causing the feature extraction to fail for that particular candidate.
-The result of these failures was that there was a smaller dataset to train the machine learning classifiers on, and a smaller dataset to make machine learning classification predictions on.
-
-    \item Build the Radio Frequency Interference (RFI) classification feature discussed by \textcite{tan} into \verb|PulsarClassifier|:
-
-    According to \textcite{tan}, by also including the classification category of RFI, the accuracy of the machine learning ensemble classifier was increased.
-The result of this feature would be three classifier output files: \verb|output.pulsars|, \verb|output.rfi|, and \verb|output.other|.
-
-    \item Use a more diverse Training Dataset:
-
-    Due to constraints on the available \verb|PFD| candidate data during this project, I was unable to use a large set of pulsar and non-pulsar candidates in the training dataset.
-By using a training dataset that is more diverse, the \verb|PulsarClassifier| will be more accurate in its predictions.
-\end{enumerate}
-
-\pagebreak
-% REFERENCES SECTION
-\section{References}
-\printbibliography[heading=none]
-
-\pagebreak
-% APPENDICES SECTION
-\begin{appendices}
-
-    \section{Methods}
-    \begin{subappendices}
-        \subsection{Feature Extraction with PulsarFeatureLab}
-
-        \subsection{Using PulsarValidator}
 
@@
     \begin{subappendices}
-        \label{sec:pulsarvalidator} 
+        \label{src:pulsarvalidator} 
         \subsection{PulsarValidator.java}
@@
     \begin{subappendices}
-        \label{sec:pulsarclassifier}
+        \label{src:pulsarclassifier}
         \subsection{PulsarClassifier.java}

### 2020-06-03 Draft.tex
Methods and appendices

@@
 
-\verb|PulsarValidator| is designed to load the positive and negative output files generated from the machine learning classification of a controlled testing dataset of pulsar candidates, and compare these files to a list of the pulsars included in the testing dataset.
+\verb|PulsarValidator| was designed to load the positive and negative output files generated from the machine learning classification of a controlled testing dataset of pulsar candidates, and compare these files to a list of the pulsars included in the testing dataset.
 The software outputs the following statistics: the number of pulsars and non-pulsars, the number of detected pulsars and non-pulsars, and the number of true positives (TP), false positives (FP), true negatives (TN), and false negatives (FN).
@@
 
-\subsection{Evaluating the LOTAAS Machine Learning Classification Tool for use with the SMART Survey}
-
-To address the Candidate Selection Problem discussed in \emph{Section 1.3} of this report, a Java Machine Learning pulsar classification tool named \verb|LOTAASClassifier| was created to classify the pulsar candidates produced by the LOFAR Tied-Array All-sky Survey (LOTAAS) \autocite{lyon}.
-Due to the similarities between the LOFAR radio telescope and the Murchison Widefield Array (MWA) radio telescope, it is logical to attempt to apply the \verb|LOTAASClassifier| tool to candidates produced by the MWA.
-
-The \verb|LOTAASClassifier| tool contains four machine learning algorithms with which the user can choose to make pulsar classifications.
-They are: the J48 (C4.5 Decision Tree \autocite{quinlan}), the Multi-Layer Perceptron, the Naive Bayes, and the Support Vector Machines (SVM) algorithms \autocite{lyon}.
-
-To begin evaluating the software, \verb|LOTAASClassifier v1.0| can be downloaded from its GitHub repository \\(\verb|https://github.com/scienceguyrob/LOTAASClassifier|) with the following UNIX terminal commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars
-$ git clone https://github.com/scienceguyrob/LOTAASClassifier.git
-\end{lstlisting}
-
-The tool's executable program can then be found by navigating to the following directory in the UNIX terminal:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/LOTAASClassifier/dist
-\end{lstlisting}
-
-\subsubsection{Evaluating LOTAASClassifier}
-
-With a successfully created machine learning classification model, it is now possible to test \verb|LOTAASClassifier| against a previously unseen (by the classifier) dataset of Murchison Widefield Array candidates whose class is also known.
-We can first remove the existing candidates from inside the \verb|PFD| files directory and delete the existing \verb|output| files.
-
-The candidates directory can then be populated by new \verb|PFD| files and we can use the `\verb|docker run|' command from \emph{Section 2.2.1} to extract the features from the new candidates.
-
-The \verb|LOTAASClassifier| tool can now make classification predictions on the new candidates by running the UNIX terminal command:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/LOTAASClassifier/dist
-$ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
-\end{lstlisting}
-
-This can be repeated for each machine learning classifier present in the \verb|LOTAASClassifier| software by changing the argument \verb|-a| from 1 through to 4.
-
-We can now run the \verb|PulsarValidator| program created in \emph{Section 2.2.1} to evaluate the accuracy of \verb|LOTAASClassifier|'s algorithms by running the command:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarValidator/target
-$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_[classifier].positive ~/pulsars/data/pfd/output_[classifier].negative
-\end{lstlisting}
-
-Where the \verb|[classifier]| variable can be changed depending on the name of the classifier algorithm being evaluated.
-The outputted validation statistics can then be compared across the algorithms to determine their usefulness with the Murchison Widefield Array.
-
-\subsubsection{Creating the PulsarClassifier Ensemble Classification Tool}
-\label{sec:methodensemble}
-According to \cite{tan}, using Machine Learning algorithms in ensemble to make pulsar classifications increases the accuracy of classifications, classifying pulsars that were often misclassified such as wide-pulse pulsars.
-
-To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars
-$ mkdir PulsarClassifier && cd PulsarClassifier
-$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
-\end{lstlisting}
-
-We can now copy the source code from \verb|LOTAASClassifier| to be included in the \verb|PulsarClassifier| software.
-
-\begin{lstlisting}[numbers=none]
-$ cp -R ~/pulsars/LOTAASClassifier/src/ ~/pulsars/PulsarClassifier/src/main/java
-\end{lstlisting}
-
-To use the WEKA suite of Machine Learning tools, we must then edit the \verb|pom.xml| file inside \verb|PulsarClassifier| to include it as a dependency, and resynchronise the project:\\
-
-\begin{lstlisting}[numbers=none, title=pom.xml, language=xml]
-...
-<dependencies>
-...
-    <dependency>
-        <groupId>nz.ac.waikato.cms.weka</groupId>
-        <artifactId>weka-stable</artifactId>
-        <version>3.8.0</version>
-    </dependency>
-...
-</dependencies>
-...
-\end{lstlisting}
-
-We now have the following basic project directory structure:
-
-\begin{lstlisting}[numbers=none]
-PulsarClassifier/
-    src/
-        main/
-            java/
-                com/jacobianmatthews/pulsarclassifier/
-                com/scienceguyrob/lotaasclassifier/
-        test/
-            java/
-                com/jacobianmatthews/pulsarclassifier
-    target/
-            ...
-    pom.xml
-\end{lstlisting}
-
-Where the new source code will be located under \\\verb|/src/main/java/com/jacobianmatthews/pulsarclassifier|.
-To introduce the ensemble classification feature, we must write four main Java classes: \\\verb|PulsarClassifier.java|,  \verb|ClassifierBuilder.java|,  \verb|ClassifierValidator.java|,  and \verb|ClassPredictor.java|.
-
-The \verb|LOTAASClassifier| tool accepts a command-line argument \verb|-a| which accepts an integer that denotes the machine learning algorithm to use in building a classification model and making predictions \autocite{lyon}.
-Therefore, we will add an algorithm into the above listed Java classes that will accept an integer value of \verb|-1| that will activate the ensemble classifier.
-
-The class \verb|ClassifierBuilder.java| handles training and building a classification model. To add ensemble classification to this class we will use the following algorithm:
+\subsection{Developing an Ensemble Machine Learning Classifier}
+
+To implement the ensemble classifier feature outlined by \textcite{tan} to the \verb|LOTAASClassifier| software, a new Java program named \verb|PulsarClassifier| was developed.
+
+\verb|PulsarClassifier| was designed so that a new `ensemble classifier' option can be chosen as the classification algorithm as well as the previously existing algorithms from \verb|LOTAASClassifier|.
+The program outputs the classification results of all machine learning classifiers from the \verb|LOTAASClassifier| program, as well as that of the new ensemble classifier.
+This was achieved by creating the following new Java classes: `PulsarClassifier', `ClassPredictor', `ClassifierBuilder', and `ClassifierValidator', and extending the existing versions of those classes from \verb|LOTAASClassifier| to maintain some of the prior methods and properties.
+
+The Java classes `ClassifierBuilder' and `ClassifierValidator' were modified such that if the user selected the ensemble classifier as the classification algorithm, the method involved in building or validating a machine learning classifier would iterate through the list of available machine learning classifiers (C4.5, Multi-Layered Perceptron, Naïve Bayes, and Support Vector Machine) to build a classification model for each ML classifier, or validate each ML classifier, respectively.
+These processes can be seen in \emph{Algorithm \ref{alg:classifierbuilder}} and \emph{Algorithm \ref{alg:classifiervalidator}}.
 
@@
     \caption{ClassifierBuilder (pseudocode)}
+    \label{alg:classifierbuilder}
     \begin{algorithmic}[1]
@@
         \EndIf
-
     \end{algorithmic}
@@
 
-See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
-
-The class \verb|ClassifierValidator.java| handles validating and testing the existing classification models.
-To implement the ensemble classifier into this class, we will use the following, similar algorithm:
-
 \begin{algorithm}[H]
     \caption{ClassifierValidator (pseudocode)}
+    \label{alg:classifiervalidator}
     \begin{algorithmic}[1]
@@
 
-See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
-
-The class \verb|ClassPredictor.java| handles making the classification predictions on new data using existing classifier models.
-We can add the ensemble classification feature to this class with the following algorithm:
-
-\begin{algorithm}[H]
+The Java class `ClassPredictor' was modified such that if the user chooses to use the ensemble classifier, a Java `ArrayList' is created to store the filepaths to the outputs of each machine learning classifier.
+The list of available machine learning classifiers is then iterated over, generating the classification predictions from each classifier and adding their outputs to the created list of output files.
+The Java classes `Classification' and `ClassificationList' are then created to be a key-value pair data class and a list of key-value classifications respectively, where the key denotes the filename of a candidate and the value denotes the number of times this candidate has been given a particular classification.
+A `ClassificationList' for positive and negative classifications are then constructed and the candidates in the positive and negative classifier output files are iterated over, adding the candidates to their respective lists and incrementing their associated value for every recurring classification.
+As discussed in \textcite{tan}, a positive classification in an ensemble classifier is generally made when a candidate has received a positive classification from 3 separate classifiers.
+To implement this selection criteria, the positive `ClassificationList' is iterated over and the candidates with an associated value less than 3 are moved into the negative `ClassificationList'.
+The remaining positive and negative `ClassificationList's are then outputted to their respective positive and negative output files for the ensemble classifier.
+This process can be seen in \emph{Algorithm \ref{alg:classpredictor}}.
+
+\begin{algorithm}
     \caption{ClassPredictor (pseudocode)}
+    \label{alg:classpredictor}
     \begin{algorithmic}[1]
@@
 
-The above algorithm preserves the individual classifiers' predictions and also makes an ensemble prediction based on all of the classifiers' predictions.
-According to \cite{tan}, it is common for ensemble machine learning classifiers to use a cut-off of three concurrent positive predictions in separate classifiers to make a positive ensemble classification.
-Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
-See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
-
-The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
-This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
-The complete source code to the \verb|PulsarClassifier| contains the following classes:
-
-\begin{lstlisting}[numbers=none]
-src/
-    main/
-        java/
-            com/jacobianmatthews/pulsarclassifier/
-                utils/
-                    Classification.java
-                    ClassificationList.java
-                    Classifiers.java
-                    Models.java
-                PulsarClassifier.java
-                ClassifierBuilder.java
-                ClassifierValidator.java
-                ClassPredictor.java
-
-            com/scienceguyrob/lotaasclassifier/
-                ...
-
-\end{lstlisting}
-
-Now that the source code for the package is complete, we can add the following lines to the \verb|pom.xml| file at the root of the project:
-
-\pagebreak
-\begin{lstlisting}[numbers=none, language=xml, title=pom.xml, basicstyle=\footnotesize\ttfamily]
-<project>
-    ...
-    <build>
-      <pluginManagement>
-        <plugins>
-          ...
-
-          <!-- Create a JAR containing the resources and dependencies -->
-          <plugin>
-            <groupId>org.apache.maven.plugins</groupId>
-            <artifactId>maven-assembly-plugin</artifactId>
-            <configuration>
-              <archive>
-                <manifest>
-                  <addClasspath>true</addClasspath>
-                  <mainClass>com.jacobianmatthews.pulsarclassifier.PulsarClassifier</mainClass>
-                </manifest>
-              </archive>
-              <descriptorRefs>
-                <descriptorRef>jar-with-dependencies</descriptorRef>
-              </descriptorRefs>
-            </configuration>
-            <executions>
-              <execution>
-                <phase>package</phase>
-                <goals>
-                  <goal>single</goal>
-                </goals>
-              </execution>
-            </executions>
-          </plugin>
-
-          ...
-        </plugins>
-      </pluginManagement>
-    </build>
-    ...
-</project>
-\end{lstlisting}
-
-This will instruct Maven to build a Java \verb|JAR| file containing the package and its WEKA library dependency. To build the package, we can run the following commands in the UNIX terminal:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarClassifier
-$ mvn assembly:single
-\end{lstlisting}
-
-The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{sec:pulsarclassifier}}.
-
-\subsubsection{Evaluating PulsarClassifier}
-
-Now that we have successfully built \verb|PulsarClassifier|, we can evaluate its usage with the Murchison Widefield Array's (MWA) candidates. We begin by:
-\begin{enumerate}[label=\roman*.] 
-    \item deleting the previous \verb|output.positive| and \verb|output.negative| files from the \verb|PFD| candidates directory; and
-    \item deleting the previous \verb|model.m| file created by the \verb|LOTAASClassifier| software.
-\end{enumerate}
-
-We can now build the ensemble classification model with the training dataset created earlier, by running the following commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd target
-$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/models -a -1
-\end{lstlisting}
-
-Where the argument \verb|-m| now denotes the path to a directory to store the various classifier models.
-Now that we have all of the classification models created, we can use the ensemble classifier to predict the class of new candidates.
-Using the feature extracted candidates compiled from \emph{Section 2.2.2}, we can run the following command:
-
-\begin{lstlisting}[numbers=none]
-$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/models -a -1
-\end{lstlisting}
-
-\verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
-We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
-
-\begin{lstlisting}[numbers=none]
-$ cd ~/pulsars/PulsarValidator/target
-$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_ensemble.positive ~/pulsars/data/pfd/output_ensemble.negative
-\end{lstlisting}
-
-The outputted validation statistics can then be compared to those created for the \verb|LOTAASClassifier| algorithms and an opinion can be formed in regards to the utility of \verb|PulsarClassifier| with the Murchison Widefield Array.
+The final modification that was made included changing the Java class `PulsarClassifier' to include the ensemble classifier as an option in the user selectable algorithms.
+Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarclassifier}} and the full Java source code can be found in \emph{Appendix \ref{src:pulsarclassifier}} or on GitHub (\verb|https://github.com/jacob-ian/PulsarClassifier.git|).
+
+\subsection{Evaluating the Machine Learning Classifiers}
+
+A set of 147 pulsar and 87 non-pulsar candidates generated by the SMART survey were then provided by N.
+Swainston to test the machine learning classifiers on Murchison Widefield Array data.
+To test all machine learning classifiers present in \verb|LOTAASClassifier|, and the ensemble classifier, the new \\\verb|PulsarClassifier| program was used.
+
+Before making predictions on the test data, it is necessary to create the machine learning classification models from the training dataset.
+Using \\\verb|PulsarClassifier|, the training dataset was used to generate the classification models for each ML classifier.
+\verb|PulsarFeatureLab| was then used to extract the machine learning features from the testing dataset of candidates.
+\verb|PulsarClassifier| was then used to classify the candidates in the testing dataset with the ensemble classifier (and hence with each of the other ML classifiers).
+For details on the use of \verb|PulsarClassifier|, see \emph{Appendix \ref{apndx:usepulsarclassifier}}.
+
+To evaluate the accuracy of the predictions of the machine learning classifiers, a list of the pulsars included in the testing dataset was created and \verb|PulsarValidator| was ran with the output files of each classifier.
+For details on the use of \verb|PulsarValidator|, see \emph{Appendix \ref{apndx:usepulsarvalidator}}.
 
@@
 
-        \subsection{Creating a Classification Model with LOTAASClassifier}
-
-        In order to use \verb|LOTAASClassifier| to classify Murchison Widefield Array candidates, we must use the Machine Learning Training Dataset created in \emph{Section 2.1} to create a classification model.
-This can be completed by running the following commands:
-
-        \begin{lstlisting}[numbers=none]
-        $ java -jar LOTAASClassifier.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/model.m -a 1
-        \end{lstlisting}
-
-        This instructs \verb|LOTAASClassifier| to create a new classification model for the J48 machine learning algorithm with the previously constructed training dataset.
-
-        To ensure that the classification model was created successfully, we can test the model against the same dataset provided by N.
-Swainston to create the training dataset.
-Using \verb|PulsarFeatureLab| we can produce a new \verb|output.arff| file with the candidates' class unedited.
-
-        \begin{lstlisting}[numbers=none]
-        $ docker run --rm -v ~/pulsars/data/pfd:/usr/src/app/PulsarFeatureLab/Data/IO jacobianm/pulsarfeaturelab:1.3.2 -d "/usr/src/app/PulsarFeatureLab/Data/IO" -c 3 -t 6 -f "/usr/src/app/PulsarFeatureLab/Data/IO/output.arff" --arff --meta
-        \end{lstlisting}
-
-        It is now possible to test the classification model with the candidate feature sets with the following commands:
-
-        \begin{lstlisting}[numbers=none]
-        $ cd ~/pulsars/LOTAASClassifier/dist
-        $ java -jar LOTAASClassifier.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/model.m -a 1
-        \end{lstlisting}
-
-        The \verb|LOTAASClassifier| tool will output two files: `\verb|output.positive|' and `\verb|output.negative|', in the same location as the input dataset.
-The J48 classification model was constructed successfully if the candidates inside the `\verb|positive|' file are the known pulsars.
+        \subsection{Developing PulsarClassifier}
+        \label{apndx:pulsarclassifier}
+        To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars
+$ mkdir PulsarClassifier && cd PulsarClassifier
+$ mvn archetype:generate -DarchetypeGroupId=org.apache.maven.archetypes -DarchetypeArtifactId=maven-archetype-quickstart -DarchetypeVersion=1.4
+\end{lstlisting}
+
+We can now copy the source code from \verb|LOTAASClassifier| to be included in the \verb|PulsarClassifier| software.
+
+\begin{lstlisting}[numbers=none]
+$ cp -R ~/pulsars/LOTAASClassifier/src/ ~/pulsars/PulsarClassifier/src/main/java
+\end{lstlisting}
+
+To use the WEKA suite of Machine Learning tools, we must then edit the \verb|pom.xml| file inside \verb|PulsarClassifier| to include it as a dependency, and resynchronise the project:\\
+
+\begin{lstlisting}[numbers=none, title=pom.xml, language=xml]
+...
+<dependencies>
+...
+    <dependency>
+        <groupId>nz.ac.waikato.cms.weka</groupId>
+        <artifactId>weka-stable</artifactId>
+        <version>3.8.0</version>
+    </dependency>
+...
+</dependencies>
+...
+\end{lstlisting}
+
+We now have the following basic project directory structure:
+
+\begin{lstlisting}[numbers=none]
+PulsarClassifier/
+    src/
+        main/
+            java/
+                com/jacobianmatthews/pulsarclassifier/
+                com/scienceguyrob/lotaasclassifier/
+        test/
+            java/
+                com/jacobianmatthews/pulsarclassifier
+    target/
+            ...
+    pom.xml
+\end{lstlisting}
+
+Where the new source code will be located under \\\verb|/src/main/java/com/jacobianmatthews/pulsarclassifier|.
+To introduce the ensemble classification feature, we must write four main Java classes: \\\verb|PulsarClassifier.java|,  \verb|ClassifierBuilder.java|,  \verb|ClassifierValidator.java|,  and \verb|ClassPredictor.java|.
+
+The \verb|LOTAASClassifier| tool accepts a command-line argument \verb|-a| which accepts an integer that denotes the machine learning algorithm to use in building a classification model and making predictions \autocite{lyon}.
+Therefore, we will add an algorithm into the above listed Java classes that will accept an integer value of \verb|-1| that will activate the ensemble classifier.
+
+The class \verb|ClassifierBuilder.java| handles training and building a classification model. To add ensemble classification to this class we will use the following algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassifierBuilder (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State buildClassifier($i$, $trainingSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Build individual classifier
+            \State buildClassifier($algorithm$, $trainingSet$, $modelPath$)
+
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
+
+The class \verb|ClassifierValidator.java| handles validating and testing the existing classification models.
+To implement the ensemble classifier into this class, we will use the following, similar algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassifierValidator (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \For{each algorithm $i=1\rightarrow 4$}
+                \Comment Loop through all classifiers
+                \State testClassifier($i$, $testSet$, $modelsDirectory$)
+            \EndFor
+        \Else 
+            \Comment Test individual classifier
+            \State testClassifier($algorithm$, $testSet$, $modelPath$)
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
+
+The class \verb|ClassPredictor.java| handles making the classification predictions on new data using existing classifier models.
+We can add the ensemble classification feature to this class with the following algorithm:
+
+\begin{algorithm}[H]
+    \caption{ClassPredictor (pseudocode)}
+    \begin{algorithmic}[1]
+        \If{$algorithm = -1$}
+            \State list = new OutputFileList()
+            \For{algorithm $i=1\rightarrow4$}
+                \Comment Loop through all classifiers
+                \State makePredictions($i$, $inputData$, $modelsDirectory$)
+                \State list.add(ClassifierOutputFiles)
+                \Comment Add output filepaths to list
+            \EndFor
+            \State positiveList = new ClassificationsList()
+            \State negativeList = new ClassificationsList()
+            \Comment Create classification lists
+            \For{each OutputFile from list}
+                \If{OutputFile is .positive}
+                    \For{each line in OutputFile}
+                        \State positiveList.add(line)
+                        \Comment Add to +ve classifications
+                    \EndFor
+                \ElsIf{OutputFile is .negative}
+                    \For{each line in OutputFile}
+                        \State negativeList.add(line)
+                        \Comment Add to -ve classifications
+                    \EndFor
+                \EndIf
+            \EndFor
+            \For{each classification in positiveList}
+                \If{classification.occurrences $< 3$}
+                    \State negativeList.add(classification)
+                    \Comment cut-off at $< 3$ classifications
+                \Else
+                    \State positiveOutput(classification)
+                    \Comment Output classified as Pulsar
+                \EndIf
+            \EndFor
+            \For{each classification in negativeList}
+                \State negativeOutput(classification)
+                \Comment Output classified as non-Pulsar
+            \EndFor
+
+        \Else 
+            \State makePredictions($algorithm$)
+            \Comment Use individual classifier
+        \EndIf
+
+    \end{algorithmic}
+\end{algorithm}
+
+The above algorithm preserves the individual classifiers' predictions and also makes an ensemble prediction based on all of the classifiers' predictions.
+According to \cite{tan}, it is common for ensemble machine learning classifiers to use a cut-off of three concurrent positive predictions in separate classifiers to make a positive ensemble classification.
+Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
+See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
+
+The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
+This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
+The complete source code to the \verb|PulsarClassifier| contains the following classes:
+
+\begin{lstlisting}[numbers=none]
+src/
+    main/
+        java/
+            com/jacobianmatthews/pulsarclassifier/
+                utils/
+                    Classification.java
+                    ClassificationList.java
+                    Classifiers.java
+                    Models.java
+                PulsarClassifier.java
+                ClassifierBuilder.java
+                ClassifierValidator.java
+                ClassPredictor.java
+
+            com/scienceguyrob/lotaasclassifier/
+                ...
+
+\end{lstlisting}
+
+Now that the source code for the package is complete, we can add the following lines to the \verb|pom.xml| file at the root of the project:
+
+\begin{lstlisting}[numbers=none, language=xml, title=pom.xml, basicstyle=\footnotesize\ttfamily]
+<project>
+    ...
+    <build>
+      <pluginManagement>
+        <plugins>
+          ...
+
+          <!-- Create a JAR containing the resources and dependencies -->
+          <plugin>
+            <groupId>org.apache.maven.plugins</groupId>
+            <artifactId>maven-assembly-plugin</artifactId>
+            <configuration>
+              <archive>
+                <manifest>
+                  <addClasspath>true</addClasspath>
+                  <mainClass>com.jacobianmatthews.pulsarclassifier.PulsarClassifier</mainClass>
+                </manifest>
+              </archive>
+              <descriptorRefs>
+                <descriptorRef>jar-with-dependencies</descriptorRef>
+              </descriptorRefs>
+            </configuration>
+            <executions>
+              <execution>
+                <phase>package</phase>
+                <goals>
+                  <goal>single</goal>
+                </goals>
+              </execution>
+            </executions>
+          </plugin>
+
+          ...
+        </plugins>
+      </pluginManagement>
+    </build>
+    ...
+</project>
+\end{lstlisting}
+
+This will instruct Maven to build a Java \verb|JAR| file containing the package and its WEKA library dependency. To build the package, we can run the following commands in the UNIX terminal:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarClassifier
+$ mvn assembly:single
+\end{lstlisting}
+
+The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{src:pulsarclassifier}}.
+
+\subsection{Using PulsarClassifier}
+\label{apndx:usepulsarclassifier}
+
+We can use \verb|PulsarClassifier| with the Murchison Widefield Array's (MWA) candidates by:
+\begin{enumerate}[label=\roman*.] 
+    \item deleting the previous \verb|output.positive| and \verb|output.negative| files from the \verb|PFD| candidates directory; and
+    \item deleting the previous \verb|model.m| file created by the \verb|LOTAASClassifier| software.
+\end{enumerate}
+
+We can now build the ensemble classification model with the training dataset created earlier, by running the following commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd target
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -t ~/pulsars/data/trainingSet.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+Where the argument \verb|-m| now denotes the path to a directory to store the various classifier models.
+Now that we have all of the classification models created, we can use the ensemble classifier to predict the class of new candidates.
+Using the feature extracted candidates compiled from \emph{Section 2.2.2}, we can run the following command:
+
+\begin{lstlisting}[numbers=none]
+$ java -jar pulsarclassifier-1.0-jar-with-dependencies.jar -p ~/pulsars/data/pfd/output.arff -m ~/pulsars/data/models -a -1
+\end{lstlisting}
+
+\verb|PulsarClassifier| will create the prediction output files for each classifier, and then the \verb|output_ensemble.positive| and \verb|output_ensemble.negative| files for the ensemble classifier.
+
+\subsection{Using PulsarValidator}
+\label{apndx:usepulsarvalidator}
+We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
+
+\begin{lstlisting}[numbers=none]
+$ cd ~/pulsars/PulsarValidator/target
+$ java -jar pulsarvalidator-1.0-full.jar -v ~/pulsars/data/pfd/pulsars.txt ~/pulsars/data/pfd/output_ensemble.positive ~/pulsars/data/pfd/output_ensemble.negative
+\end{lstlisting}
+
+The outputted validation statistics can then be compared to those created for the \verb|LOTAASClassifier| algorithms and an opinion can be formed in regards to the utility of \verb|PulsarClassifier| with the Murchison Widefield Array.
 

### 2020-06-06 Draft.tex
Final report

@@
 \usepackage[title,toc,page]{appendix}
+\usepackage{arydshln}
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=black,
+    urlcolor=blue,
+    linktoc=all,
+    citecolor=black
+}
 
@@
 \title{\large{Curtin University} \\ \large{Curtin Institute of Radio Astronomy} \\ \large{Physics Project 1} \\ \vspace*{20px} \textbf{\LARGE{Finding New Pulsars Using Machine Learning}}\vspace*{10px}}
-\author{\vspace*{20px} Jacob Ian Matthews \\ \\ Draft}
+\author{\vspace*{20px} Jacob Ian Matthews}
 
@@
     \thispagestyle{empty}
+
+    \centering
+    \textbf{Supervisors} \\\vspace*{5px}Dr Sam McSweeney and Dr Ramesh Bhat\\
 
@@
 
+\pagebreak
 \subsection{Background Theory}
@@
 
-To answer the question of ``what is a pulsar?" we must first investigate the evolution and death of stars.
-
-A star can form when a cloud of hydrogen gas in the interstellar medium (ISM) collects mass over millions of years; as the mass of the gas cloud increases, its gravitational pull to gather more mass also increases \autocite{maoz}.
-This proto-star will eventually reach a critical mass in which the pressure of gravity within the gas causes enough friction between the gas particles to generate the required heat (thermal pressure) to begin fusing the hydrogen atoms into helium \autocite{maoz}.
-This marks the beginning of the star's main sequence lifetime.
-Once the star has fused all of the available hydrogen gas in its core, the star will begin fusing helium into carbon and its outer envelope will expand, moving the star into its "red-giant" phase \autocite{maoz}.
-If the initial mass of the star was greater than 8 times the mass of the Sun (i.e.
-$8M_{\odot}$), the star will continue to fuse the elements in its core until it reaches a core of iron.
-At this point phenomena called nuclear photodisintegration and neutronization occurs, the latter of which causes electrons and photons to combine and form neutrons and anti-neutrinos \autocite{maoz}.
-Neutronization can be shown as:
-
-$$ e^{-}+p\rightarrow n + \nu_e$$
-
-This process removes the electron degeneracy pressure in the core of the star (a pressure which balances the star's gravitational pressure), causing the star to collapse under its own gravity in a timeframe of 0.1 seconds \autocite{maoz}.
-The gravitational collapse stops once the gravitational pressure of the star is balanced by the neutron degeneracy pressure, i.e.
-the pressure from pushing neutrons together.
-The remaining star is incredibly dense, with a mass of approximately $1.4M_{\odot}$ and a radius of around 11km.
-This is called a neutron star \autocite{maoz}.
-
-Prior to the collapse of the star, we can imagine the star to be rotating at an angular velocity of $\omega_1$.
-We know from the conservation of angular momentum that when the radius of a rotating object decreases, the angular velocity will increase (a spinning ice skater pulling their arms in close increases the speed of their spinning).
-We can therefore show that the angular velocity of the star after the gravitational collapse, $\omega_2$, is much greater than the prior angular velocity:
-
-$$L_1 = L_2$$ where $L$ is the angular momentum, $L_1=I_1\omega_1$ and $L_2=I_2\omega_2$. Therefore:
-
-$$ I_1 \omega_1 = I_2 \omega_2 $$
-
-$$\omega_2 = \frac{I_1}{I_2}\omega_1$$
-
-Assuming the star is a sphere, its moment of inertia, $I$ is:
-
-$$I = \frac{2}{5}MR^2$$ where $M$ is the mass of the star and $R$ is the radius of the star. We can thus show:
-
-$$\omega_2 = \frac{\frac{2}{5}MR_1^2}{\frac{2}{5}MR_2^2}\omega_1$$
-
-$$\omega_2 = \left(\frac{R_1}{R_2}\right)^2\omega_1$$ where $R_1 \gg R_2$.
-We are left with a neutron star with a very large angular velocity.
-Analogous to the angular velocity of the star, the magnetic field of the star is also amplified.
-The ionised gas in the iron core of the star, which generates a magnetic field, is compressed by the gravitational collapse, forcing the flux of the magnetic field to be amplified such that the field strength is approximately $10^{10}$ times stronger in the neutron star compared to during the star's main sequence lifetime \autocite{maoz}.
-
-If the rotation of the neutron star is misaligned with the axis of the magnetic field by an angle $\theta$, the spinning magnetic dipole will radiate electromagnetic waves \autocite{maoz}.
-As the neutron star rotates, the radiated electromagnetic waves will periodically sweep across the line of sight of an observer, creating a pulse of light.
-See Figure \ref{fig:pulsar1}.
-We can therefore define a pulsar as a rapidly rotating neutron star that appears to periodically emit electromagnetic waves \autocite{maoz,lorimer,swainston}.
+Pulsars were first detected in 1967 at the Mullard Radio Astronomy Observatory when a periodically pulsing radio source was discovered \autocite{hewish:pulsar}.
+The pulsing radio source was found to not be man-made or of terrestrial nature, as it could only be observed at a particular declination and right ascension \autocite{hewish:pulsar}.
+Pulsars were thus suggested to be either rotating white dwarf stars or neutron stars \autocite{hewish:pulsar,gold:pulsar}, the latter suggestion of which was later supported by the works of \textcite{gold:pulsar}.
+\textcite{gold:pulsar} found that pulsars were more often detected in supernova areas -- supernovae being the producers of neutron stars -- and that pulsars with faster rotations corresponded to younger neutron stars.
+The theory that a pulsar is a rapidly rotating neutron star was further confirmed by the works of \textcite{ostriker:pulsar}, as well as discovering that pulsars possess a dipole magnetic field that isn't parallel to its rotation axis.
+A diagram of a pulsar and its magnetic field can be seen in \emph{Figure \ref{fig:pulsar1}}.
 
@@
 
-While some pulsars, like the Crab Pulsar \autocite{maoz}, emit electromagnetic waves in the visible spectrum and can therefore be detected by an optical telescope, the majority of pulsar emission is invisible to the human eye and requires a radio telescope to be detected.
-
-\subsubsection{What is a Pulsar Profile?}
-\subsubsection{What is multi-path scattering?}
-\subsubsection{What is a Pulsar Dispersion Measure?}
-\subsubsection{What is a Radio Telescope and how do they work?}
-\subsubsection{What is the Murchison Widefield Array?}
-\subsubsection{Why are we conducting sky surveys?}
-\subsubsection{How is a sky survey conducted with the Murchison Widefield Array?}
-\subsubsection{What is tied-array beamforming?}
-\subsubsection{How many Pulsar candidates are found in a Murchison Widefield Array sky survey?}
-\subsubsection{How long do sky surveys take?}
-\subsubsection{How much data is created from a sky survey?}
-\subsubsection{What is Radio Frequency Interference?}
-\subsubsection{What is a Signal-to-Noise Ratio?}
-\subsubsection{What is PRESTO and a .PFD file?}
-\subsubsection{What is Machine Learning?}
-\subsubsection{How does Machine Learning work?}
-\subsubsection{Why do we need to use Machine Learning in finding new Pulsars?}
-\subsubsection{Why is this particular Machine Learning Classifier used?}
+When a star reaches the end of its life, if its initial mass was greater than eight times the mass of the sun, i.e.
+$8M_{\odot}$, the star will likely supernova, exploding its outer envelope into the surrounding space, leaving the gravitationally collapsed core of the star \autocite{maoz}.
+This is a neutron star.
+Using the conservation of angular momentum, we can prove that the collapsed neutron star will have a speed of rotation much greater than the star did prior to the its gravitational collapse.
+If one considers an ice skater rotating with their arms stretched out, we intuitively know that their speed of rotation will increase if their arms are brought in closer to their body.
+The same effect applies for a star: if prior to the star's collapse it is rotating at an angular velocity $\omega_1$, the angular velocity $\omega_2$ after the star collapses to a radius of ~11km from a radius thousands of times larger, will be much greater \autocite{maoz}.
+
+Despite our understanding of the formation of neutron stars and their rotation, the nature of their electromagnetic wave emission is still an active area of research \autocite{lorimer}.
+The reason that pulsars appear to emit a pulse of radio waves is due to a process called the `lighthouse effect': as the neutron star rotates, the radiated electromagnetic waves sweep across the sky, crossing the line of sight of an observer and producing a pulse-like effect \autocite{lorimer}.
+When the radio wave passes the line of sight of a radio telescope, the pulse can be recorded.
+An Integrated Pulse Profile can then be generated from the pulse recorded by the telescope by a process called folding, where a number of separate observations of the pulse can be `stacked' on top of each other to produce a clear representation of the pulse \autocite{helfand:profiles}.
+An example of an integrated pulse profile can be seen in \emph{Figure \ref{fig:profile}}.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=5cm]{PSR_0459-0210-profile.jpg}
+    \begin{center}
+    \caption{Integrated Pulse Profile of Pulsar 0459-0210 \autocite{swainston:data}.}
+    \label{fig:profile}
+    \end{center}
+\end{figure}
+
+\subsubsection{Sky Surveys}
+
+When completing sky surveys in radio astronomy, it is common to detect many examples of radio frequency interference and noise \autocite{hewish:pulsar,lorimer,lyon,tan}.
+Radio frequency interference (RFI) is any radio signal that has been unintentionally detected; it normally arises from electrical devices with a periodic nature, such as devices with AC currents, communication systems like radar, or from electrical storms \autocite{lorimer}.
+Noise, on the other hand, can be detections of the Cosmic Microwave Background (depending on the sensitivity of the radio telescope), or detections of radio waves produced by the electronics of the telescope \autocite{lorimer}.
+An example of an integrated pulse profile produced by radio frequency interference and noise can be seen in \emph{Figure \ref{fig:rfinoise}}.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=5cm]{rfi.png}
+    \includegraphics[width=5cm]{noise.png}
+    \begin{center}
+    \caption{Examples of RFI (left) and Noise (right) \autocite{swainston:data}.}
+    \label{fig:rfinoise}
+    \end{center}
+\end{figure}
+
+It is scientifically important to survey the skies to find new pulsars for a multitude of reasons.
+For example: due to their extremely reliable periodicity, pulsars can be used as astronomical clocks of high accuracy \autocite{matsakis:pulars}.
+Also, due to the massive gravitational fields surrounding pulsars, binary pulsars are the definitive area in which to test gravitational theories in the strong-field, such as Einstein's theory of General Relativity, and future research into quantum gravity \autocite{lorimer}.
+
+Throughout the history of pulsar discovery, as the sky survey techniques of detection and radio telescope technology has improved, the number of candidates detected has grown at a very fast rate \autocite{lyon}.
+The growth rate of the number of candidates stands to increase further with the development of extremely large radio telescopes such as the Square Kilometre Array (SKA) \autocite{lyon}.
+This introduces a new problem to sky surveying: the candidate selection problem.
+The candidate selection problem occurs when there are too many detected pulsar candidates to be classified as pulsar or as a non-pulsar than can be feasibly examined by human eyes \autocite{lyon}.
+
+To attempt to solve the candidate selection problem, \textcite{lyon} turned to using a machine learning classifier as an intelligent filter that will filter out the candidates that are radio frequency interference or noise, reducing the candidates to be classified by a human to a more manageable number.
+
+\subsubsection{Machine Learning}
+
+\textcite{valiant} first described machine learning as a function in which a computer completes a task that hasn't been explicitly programmed, it has instead learned to do so.
+A supervised learning classifier is a function in which a machine learns examples of a particular class and then classifies other inputted data based on the learned model \autocite{dietterich}.
+
+In addressing the candidate selection problem, \textcite{lyon} created a program named \verb|LOTAASClassifier| which contains four separate machine learning algorithms that can be chosen from:
+\begin{enumerate}
+    \item The C4.5 Decision Tree;
+    \item the Multilayered Perceptron;
+    \item the Naive Bayes classifier; and
+    \item the Support Vector Machine.
+\end{enumerate}
+
+The machine learning classifiers from \verb|LOTAASClassifier| generate a classification model from an inputted training dataset, and then they can make classification predictions on the class of pulsar candidates \autocite{lyon}.
+The training dataset used by \textcite{lyon} contained a set of pulsars, radio frequency interference, and noise.
+This allows the machine learning classifiers to distinctly identify what is and isn't a pulsar.
+
+By using the machine learning classifiers, \textcite{lyon} was able to accurately predict the class of the candidates 97.1\%.
+of the time, reducing the number of candidates that had to be manually classified.
 
@@
 The free Python software created by \textcite{lyon}, \verb|PulsarFeatureLab|, was used to process the PRESTO Prepfold \verb|PFD| pulsar candidate files, extracting the above 20 machine learning features from each candidate into a single file of WEKA Data Mining \verb|ARFF| filetype.
-To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software were unaffected by the host operating system, a containerised virtual operating system was created using the free software Docker (\verb|https://docker.com|) and the pulsar feature extraction software was thus ran using a bind mounted volume.
+To create a closed software environment in which the dependencies of the \verb|PulsarFeatureLab| software were unaffected by the host operating system, a containerised virtual operating system was created using the free software Docker (\href{https://docker.com}{https://docker.com}) and the pulsar feature extraction software was thus ran using a bind mounted volume.
 For further details on how this was achieved, see \emph{Appendix \ref{apndx:pulsarfeaturelab}}.
@@
 This process can be seen in \emph{Algorithm \ref{alg:validator}}.
-Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarvalidator}}, and the full Java source code can be found in \emph{Appendix \ref{src:pulsarvalidator}} or on GitHub (\verb|https://github.com/jacob-ian/PulsarValidator.git|).
+Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarvalidator}}, and the full Java source code can be found in \emph{Appendix \ref{src:pulsarvalidator}} or on GitHub (\href{https://github.com/jacob-ian/PulsarValidator.git}{https://github.com/jacob-ian/PulsarValidator.git}).
 
@@
 The final modification that was made included changing the Java class `PulsarClassifier' to include the ensemble classifier as an option in the user selectable algorithms.
-Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarclassifier}} and the full Java source code can be found in \emph{Appendix \ref{src:pulsarclassifier}} or on GitHub (\verb|https://github.com/jacob-ian/PulsarClassifier.git|).
+Further details on the development of this software can be found in \emph{Appendix \ref{apndx:pulsarclassifier}} and the full Java source code can be found in \emph{Appendix \ref{src:pulsarclassifier}} or on GitHub (\href{https://github.com/jacob-ian/PulsarClassifier.git}{https://github.com/jacob-ian/PulsarClassifier.git}).
 
@@
 
-\subsection{Combined Analyses}
-
-A table containing the pulsar and non-pulsar classification success rates of all algorithms and the ensemble classifier can be found below:
+\subsection{Compilation of Results and Analyses}
+
+A table containing the number of true and false positives and negatives for each classifier can be found below in \emph{Table \ref{tab:compiled}}:
+
+\begin{table}[H]
+    \centering
+
+    \caption{Compiled Results of the Machine Learning Classifiers}
+
+    \begin{framed}
+        \begin{tabular}{l c c c c}
+            & \multicolumn{2}{c}{Pulsars} & \multicolumn{2}{c}{Non-Pulsars} \\
+            Classifier & TP & FN & TN & FP \\
+            \hline
+            \hline
+            LOTAASClassifier &  &  & \\
+            \hline
+            J48 & 131 & 16 & 72 & 15 \\
+            MLP & 123 & 24 & 85 & 2 \\
+            NB & 118 & 29 & 86 & 1 \\
+            SVM & 97 & 50 & 87 & 0 \\
+            \hline
+            PulsarClassifier &  &  & \\
+            \hline
+            Ensemble & 112 & 35 & 87 & 0 \\
+            \hline
+            \hline
+        \end{tabular}
+
+        \vspace{8px}
+        TP: Number of True Positives.\\
+        FN: Number of False Negatives.\\
+        TN: Number of True Negatives.\\
+        FP: Number of False Positives. \\
+    \end{framed}
+    \label{tab:compiled}
+\end{table}
+
+A table containing the pulsar and non-pulsar classification success rates of all algorithms and the ensemble classifier can be found below in \emph{Table \ref{tab:analyses}}:
 
@@
             SVM & 65.98\% & 100.00\% & 82.99\% \\
+            \hdashline 
+            \emph{Average} & 79.76\% & 94.83\% & 87.30\% \\
             \hline
@@
             Ensemble & 76.19\% & 100.00\% & 88.10\% \\
+            \hline
+            \hline
         \end{tabular}
 
-        \vspace{5px}
+        \vspace{8px}
         $R_p$: Success rate of pulsar classification.\\
         $R_{np}$: Success rate of non-pulsar classification. \\
+        $Combined$: Combined success rate (total accuracy).\\
     \end{framed}
@@
 \end{enumerate}
-\autocite{swainston}. While the classification pipeline itself appears to be optimal, I have identified a few issues with the previous attempts at CIRA in using the machine learning classifier.
+\autocite{swainston:git}. While the classification pipeline itself appears to be optimal, I have identified a few issues with the previous attempts at CIRA in using the machine learning classifier.
 
@@
 
-In the pipeline provided by \textcite{swainston}, it appears that CIRA has been attempting to use the training dataset generated for the LOFAR Tied-Array All-Sky Survey included with the \verb|LOTAASClassifier| software, for pulsar candidates generated in the SMART survey.
+In the pipeline provided by \textcite{swainston:git}, it appears that CIRA has been attempting to use the training dataset generated for the LOFAR Tied-Array All-Sky Survey included with the \verb|LOTAASClassifier| software, for pulsar candidates generated in the SMART survey.
 In itself, this may not present issues, however due to the unknown mismatch in the machine learning software, an issue of feature dimensions occurs.
@@
 As seen in Table \ref{tab:analyses} from \emph{Section 3.4}, the J48 algorithm does not appear to be optimal in combined pulsar and non-pulsar classification.
-To fix this issue, an ensemble machine learning classifier was created in \emph{Section 2.2.4} to replace the \verb|LOTAASClassifier| software.
+To fix this issue, an ensemble machine learning classifier was created in \emph{Section 2.3} to replace the \verb|LOTAASClassifier| software.
 
@@
         \begin{enumerate}[label=\roman*.]
-            \item use an image of Alpine Linux with \verb|git| preinstalled to download the \verb|PulsarFeatureLab| software from GitHub \\(\verb|https://github.com/scienceguyrob/PulsarFeatureLab|);
+            \item use an image of Alpine Linux with \verb|git| preinstalled to download the \verb|PulsarFeatureLab| software from GitHub \\(https://github.com/scienceguyrob/PulsarFeatureLab);
             \item create a directory inside the downloaded software to store the input and output data;
@@
 
-        For future development of this project, the Docker image \\\verb|jacobianm/pulsarfeaturelab:1.3.2| is available on Docker Hub\\(\verb|https://hub.docker.com|) and will be automatically downloaded when running the \verb|docker run| command below.
+        For future development of this project, the Docker image \\\verb|jacobianm/pulsarfeaturelab:1.3.2| is available on Docker Hub\\(https://hub.docker.com) and will be automatically downloaded when running the \verb|docker run| command below.
 Candidate \verb|PFD| files of known pulsars and non-pulsars detected by the Murchison Widefield Array (MWA) can now populate the above created directory, and the following command can be ran to extract the features from the candidates:
@@
         \label{apndx:pulsarvalidator}
-        We begin by creating a new Java project using the free software Maven (\verb|https://maven.apache.org|) by running the following commands in a UNIX terminal:
+        We begin by creating a new Java project using the free software Maven (https://maven.apache.org) by running the following commands in a UNIX terminal:
 
@@
         We can then use a simple conditional statement after this function is ran to check if the \verb|Boolean ValidationMode| has been set to \verb|true|, to determine whether to continue the validation.
-The complete Java class \verb|PulsarValidator.java| can be seen in \emph{Appendix \ref{sec:pulsarvalidator}.1}.
+The complete Java class \verb|PulsarValidator.java| can be seen in \emph{Appendix \ref{src:pulsarvalidator:entry}}.
 
@@
 
-        The complete Java class for \verb|ValidationMode.java| can be found in \emph{Appendix 7.2.2}, and its supplementary classes in \emph{Appendix 7.2}.
+        The complete Java class for \verb|ValidationMode.java| can be found in \emph{Appendix \ref{src:pulsarvalidator:mode}}.
 
@@
         This will produce the file: \verb|/target/pulsarvalidator-1.0-full.jar|, which is an executable Java program.
-The complete source code for \verb|PulsarValidator| can be found in \emph{Appendix 7.2} or at \\\verb|https://github.com/jacob-ian/PulsarValidator.git|.
+The complete source code for \verb|PulsarValidator| can be found in \emph{Appendix \ref{src:pulsarvalidator}} or at \\https://github.com/jacob-ian/PulsarValidator.git.
 
@@
         \label{apndx:pulsarclassifier}
-        To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (\verb|https://maven.apache.org|).
+        To build the ensemble classification feature into the existing \verb|LOTAASClassifier| tool, we can first begin by creating a new Java project named \verb|PulsarClassifier| using the free software, Maven (https://maven.apache.org).
 
@@
 
-See \emph{Appendix \ref{sec:pulsarclassifier}.2} for the complete \verb|ClassifierBuilder.java| class.
+See \emph{Appendix \ref{src:pulsarclassifier:builder}} for the complete \verb|ClassifierBuilder.java| class.
 
@@
 
-See \emph{Appendix \ref{sec:pulsarclassifier}.3} for the complete \verb|ClassifierValidator.java| class.
+See \emph{Appendix \ref{src:pulsarclassifier:validator}} for the complete \verb|ClassifierValidator.java| class.
 
@@
 Therefore, for a candidate to be classified as a pulsar with the ensemble classifier it must first be classified as a pulsar by three of the underlying machine learning classifiers.
-See \emph{Appendix \ref{sec:pulsarclassifier}.4} for the complete \verb|ClassPredictor.java| class.
+See \emph{Appendix \ref{src:pulsarclassifier:predictor}} for the complete \verb|ClassPredictor.java| class.
 
 The final class to add the ensemble classifier feature to is the entry point of the program, \verb|PulsarClassifier.java|.
-This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{sec:pulsarclassifier}.1}.
+This class only requires changes to the command-line inputs and outputs, so the completed Java class can be found in \emph{Appendix \ref{src:pulsarclassifier:entry}}.
 The complete source code to the \verb|PulsarClassifier| contains the following classes:
@@
 
-The complete source code and build of \verb|PulsarClassifier| can be found at \verb|https://github.com/jacob-ian/PulsarClassifier.git|, or in \emph{Appendix \ref{src:pulsarclassifier}}.
+The complete source code and build of \verb|PulsarClassifier| can be found at https://github.com/jacob-ian/PulsarClassifier.git, or in \emph{Appendix \ref{src:pulsarclassifier}}.
 
@@
 \label{apndx:usepulsarvalidator}
-We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Section \ref{sec:methodvalidate}} by running the commands:
+We can validate the ensemble classifier with the \verb|PulsarValidator| program created in \emph{Appendix \ref{apndx:pulsarvalidator}} by running the commands:
 
@@
         \subsection{PulsarValidator.java}
+        \label{src:pulsarvalidator:entry}
         \lstinputlisting[title=PulsarValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/PulsarValidator.java}
@@
         \subsection{ValidationMode.java}
+        \label{src:pulsarvalidator:mode}
         \lstinputlisting[title=ValidationMode.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarvalidator/ValidationMode.java}
@@
         \subsection{PulsarClassifier.java}
-        \lstinputlisting[title=PulsarClassifier.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/PulsarClassifier.java}
+        \label{src:pulsarclassifier:entry}
+        \lstinputlisting[title=PulsarClassifier.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em, literate={*}{{*\allowbreak}}1]{code/jacobianmatthews/pulsarclassifier/PulsarClassifier.java}
 
@@
         \subsection{ClassifierBuilder.java}
+        \label{src:pulsarclassifier:builder}
         \lstinputlisting[title=ClassifierBuilder.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierBuilder.java}
@@
         \subsection{ClassifierValidator.java}
+        \label{src:pulsarclassifier:validator}
         \lstinputlisting[title=ClassifierValidator.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassifierValidator.java}
@@
         \subsection{ClassPredictor.java}
+        \label{src:pulsarclassifier:predictor}
         \lstinputlisting[title=ClassPredictor.java, language=Java, basicstyle=\footnotesize\ttfamily, breaklines=true, framexleftmargin=2.5em]{code/jacobianmatthews/pulsarclassifier/ClassPredictor.java}
